---
title: "Human value analysis_ver2"
author: "Ellie Jeong"
date: "`r Sys.time()`"
output:
  html_document:
    fig_caption: yes
    highlight: pygments
    number_sections: yes
    theme: spacelab
    toc: yes
    toc_float:
      smooth_scroll: no
  pdf_document:
    toc: yes
    toc_depth: '5'
always_allow_html: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA,  warning = FALSE, message = FALSE)
```

```{r echo=FALSE}
# load packages and data
library(readr)
library(dplyr)
library(DT)
library(tidytext)
library(forcats)
library(ggplot2)
library(lubridate)
library(readr)
library(data.table)
library(tidytext)
library(entropy)
library(reshape2)
library(scales)
library(dplyr)
library(tm)
library(rapport)
library(knitr)
library(kableExtra)
library(corpus)
library(cowplot)
library(gridExtra)
library(caret)
library(rcompanion)
library(pROC)
library(ngram)
library(urltools)
library(tidyverse)
library(readxl)
library(trend)
library(data.table)
library(DT)
library(ggsci)
library(HH)
library(cluster)
library(factoextra)
library(imputeTS)
library(corrplot)
library(foreign) 
library(lavaan)
library(semPlot)

#setwd("C:/Users/hp/iCloudDrive/Desktop/Research resources/Citizen science/Data")
setwd("~/Library/CloudStorage/Box-Box/Research/Zoo Engagement Survey Pt 2/Data/Human Values Research [Ellie]/Data")
hv_analysis <- read_csv("values_analysis.csv")
```

# Human value prioritization: Descriptive statistics

Prioritize 10 Human Values of different demographic groups (gender/age/ethnicity/education level/income level)
```{r}

```

## Gender

```{r pressure3}
hv_gender <- hv_analysis %>%
  group_by(Gender_Select) %>%
  summarise(ACHIEVEMENT = mean(ACHIEVEMENT_final_score, na.rm = TRUE), BENEVOLENCE = mean(BENEVOLENCE_final_score, na.rm = TRUE), CONFORMITY = mean(CONFORMITY_final_score, na.rm = TRUE), HEDONISM = mean(HEDONISM_final_score, na.rm = TRUE), POWER = mean(POWER_final_score, na.rm = TRUE), SECURITY = mean(SECURITY_final_score, na.rm = TRUE), SELF_DIRECTION = mean(`SELF DIRECTION_final_score`, na.rm = TRUE), STIMULATION = mean(STIMULATION_final_score, na.rm = TRUE), TRADITION = mean(TRADITION_final_score, na.rm = TRUE), UNIVERSALISM = mean(UNIVERSALISM_final_score, na.rm = TRUE))
hv_gender <- as.data.frame(hv_gender)
hv_gender_rev <- t(hv_gender)
hv_gender_rev <- hv_gender_rev[-1,]
hv_gender_rev <- hv_gender_rev[,c(1,2)]
colnames(hv_gender_rev) <- c("Female", "Male")
hv_gender_rev <- as.data.frame(hv_gender_rev)
hv_gender_rev$Female <- as.numeric(hv_gender_rev$Female)
hv_gender_rev$Male <- as.numeric(hv_gender_rev$Male)
```
 * Top 3 values of female group: ACHIEVEMENT > SELF-DIRECTION > SECURITY
 * Top 3 values of male group: ACHIEVEMENT > SECURITY > SELF-DIRECTION 
 * Values in lower ranks for both groups: POWER < TRADITION < UNIVERSALISM
```{r pressure2}
#Gender count table
t_gender <- datatable(hv_analysis %>%  
                        filter (Gender_Select != "NA") %>%
                        group_by(Gender_Select) %>% 
                        tally() %>% 
                        arrange(desc(n)) %>%
                        mutate(freq = round(n / sum(n),digits=2)))
t_gender
#Gender bar graph
bar_gender_F <- ggplot(hv_gender_rev, aes(x=reorder(rownames(hv_gender_rev),-Female), y=Female))+geom_bar(stat="identity", fill="red")+xlab("Human values")+ylab("Mean")+ggtitle("Female human value prioritization") + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))  
bar_gender_F
bar_gender_M <- ggplot(hv_gender_rev, aes(x=reorder(rownames(hv_gender_rev),-Male), y=Male))+geom_bar(stat="identity", fill="blue")+xlab("Human values")+ylab("Mean")+ggtitle("Male human value prioritization")+ theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))
bar_gender_M
```

## Age
 * Age groups are created according to the below criteria
    + Young: 18~39
    + Middle-aged: 40~65
    + Old: 66~99
 
```{r}
#Age
hv_age <- hv_analysis %>% 
  mutate(Age_g=ifelse(Age<40, "Young", 
                        ifelse(Age<66, "Middle", "Old")))
hv_age2 <- hv_age %>%
  group_by(Age_g) %>%
  summarise(ACHIEVEMENT = mean(ACHIEVEMENT_final_score, na.rm = TRUE), BENEVOLENCE = mean(BENEVOLENCE_final_score, na.rm = TRUE), CONFORMITY = mean(CONFORMITY_final_score, na.rm = TRUE), HEDONISM = mean(HEDONISM_final_score, na.rm = TRUE), POWER = mean(POWER_final_score, na.rm = TRUE), SECURITY = mean(SECURITY_final_score, na.rm = TRUE), SELF_DIRECTION = mean(`SELF DIRECTION_final_score`, na.rm = TRUE), STIMULATION = mean(STIMULATION_final_score, na.rm = TRUE), TRADITION = mean(TRADITION_final_score, na.rm = TRUE), UNIVERSALISM = mean(UNIVERSALISM_final_score, na.rm = TRUE))%>% 
  filter(Age_g != "NA")
hv_age_rev <- t(hv_age2)
hv_age_rev <- hv_age_rev[-1,]
colnames(hv_age_rev) <- c("Middle", "Old", "Young")
hv_age_rev <- as.data.frame(hv_age_rev)
hv_age_rev$Middle <- as.numeric(hv_age_rev$Middle)
hv_age_rev$Old <- as.numeric(hv_age_rev$Old)
hv_age_rev$Young <- as.numeric(hv_age_rev$Young)
```
 * Top 3 values of young people: ACHIEVEMENT > SECURITY > SELF-DIRECTION 
 * Top 3 values of middle-aged people: ACHIEVEMENT > SELF-DIRECTION > SECURITY
 * Top 3 values of old people: ACHIEVEMENT > SELF-DIRECTION > SECURITY
 * Values in lower ranks for all age groups: POWER < TRADITION < UNIVERSALISM
```{r}
#Age count table
t_age <- datatable(hv_age %>%  
                     filter (Age_g != "NA") %>%
                     group_by(Age_g) %>% 
                     tally() %>% 
                     arrange(desc(n)) %>%
                     mutate(freq = round(n / sum(n),digits=2)))
t_age
#Age bar graph
bar_age_Y <- ggplot(hv_age_rev, aes(x=reorder(rownames(hv_age_rev),-Young), y=Young))+geom_bar(stat="identity", fill="#D55E00")+xlab("Human values")+ylab("Mean")+ggtitle("Young group human value prioritization")+ theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))
bar_age_Y
bar_age_M <- ggplot(hv_age_rev, aes(x=reorder(rownames(hv_age_rev),-Middle), y=Middle))+geom_bar(stat="identity", fill="#0072B2")+xlab("Human values")+ylab("Mean")+ggtitle("Middle-aged group human value prioritization")+ theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))
bar_age_M
bar_age_O <- ggplot(hv_age_rev, aes(x=reorder(rownames(hv_age_rev),-Old), y=Old))+geom_bar(stat="identity", fill="#CC79A7")+xlab("Human values")+ylab("Mean")+ggtitle("Old group human value prioritization")+ theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))
bar_age_O
```

## Ethnicity

```{r}
hv_eth <- hv_analysis %>% filter(Ethnicity_Select %in% c("White (A person having origins in any of the original peoples of Europe, the Middle East, or North Africa.)","Asian (A person having origins in any of the original peoples of the Far East, Southeast Asia, or the Indian subcontinent)","Black (A person having origins in any of the black racial groups of Africa.)","Hispanic/Latino/Spanish origin (A person of Cuban, Mexican, Puerto Rican, South or Central American, or other Spanish culture or origin, regardless of race)") )
hv_eth <- hv_eth %>%
  group_by(Ethnicity_Select) %>%
  summarise(ACHIEVEMENT = mean(ACHIEVEMENT_final_score, na.rm = TRUE), BENEVOLENCE = mean(BENEVOLENCE_final_score, na.rm = TRUE), CONFORMITY = mean(CONFORMITY_final_score, na.rm = TRUE), HEDONISM = mean(HEDONISM_final_score, na.rm = TRUE), POWER = mean(POWER_final_score, na.rm = TRUE), SECURITY = mean(SECURITY_final_score, na.rm = TRUE), SELF_DIRECTION = mean(`SELF DIRECTION_final_score`, na.rm = TRUE), STIMULATION = mean(STIMULATION_final_score, na.rm = TRUE), TRADITION = mean(TRADITION_final_score, na.rm = TRUE), UNIVERSALISM = mean(UNIVERSALISM_final_score, na.rm = TRUE))
hv_eth_rev <- t(hv_eth)
hv_eth_rev <- hv_eth_rev[-1,]
hv_eth_rev <- as.data.frame(hv_eth_rev)
colnames(hv_eth_rev) <- c("Asian", "Black", "Hispanic", "White")
hv_eth_rev$Asian <- as.numeric(hv_eth_rev$Asian)
hv_eth_rev$Black <- as.numeric(hv_eth_rev$Black)
hv_eth_rev$Hispanic <- as.numeric(hv_eth_rev$Hispanic)
hv_eth_rev$White <- as.numeric(hv_eth_rev$White)
```
 * Top 3 values of Asian: ACHIEVEMENT > SECURITY > SELF-DIRECTION 
 * Top 3 values of Black: ACHIEVEMENT > BENEVOLENCE > SECURITY
 * Top 3 values of Hispanic/Latino/Spanish origin: ACHIEVEMENT > SELF-DIRECTION > SECURITY
 * Top 3 values of White: ACHIEVEMENT > SECURITY > SELF-DIRECTION
 * Values in lower ranks for all age groups: POWER < TRADITION < UNIVERSALISM
```{r}
#Ethnicity count table
t_eth <- datatable(hv_analysis %>%  
                     filter (Ethnicity_Select %in% c("White (A person having origins in any of the original peoples of Europe, the Middle East, or North Africa.)","Asian (A person having origins in any of the original peoples of the Far East, Southeast Asia, or the Indian subcontinent)","Black (A person having origins in any of the black racial groups of Africa.)","Hispanic/Latino/Spanish origin (A person of Cuban, Mexican, Puerto Rican, South or Central American, or other Spanish culture or origin, regardless of race)") ) %>%
                     group_by(Ethnicity_Select) %>% 
                     tally() %>% 
                     arrange(desc(n)) %>%
                     mutate(freq = round(n / sum(n),digits=2)))
t_eth
#Ethnicity bar graph
bar_eth_A <- ggplot(hv_eth_rev, aes(x=reorder(rownames(hv_eth_rev),-Asian), y=Asian))+geom_bar(stat="identity", fill="#E69F00")+xlab("Human values")+ylab("Mean")+ggtitle("Asian group human value prioritization")+ theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))
bar_eth_A
bar_eth_B <- ggplot(hv_eth_rev, aes(x=reorder(rownames(hv_eth_rev),-Black), y=Black))+geom_bar(stat="identity", fill="#56B4E9")+xlab("Human values")+ylab("Mean")+ggtitle("Black group human value prioritization")+ theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))
bar_eth_B
bar_eth_H <- ggplot(hv_eth_rev, aes(x=reorder(rownames(hv_eth_rev),-Hispanic), y=Hispanic))+geom_bar(stat="identity", fill="#009E73")+xlab("Human values")+ylab("Mean")+ggtitle("Hispanic group human value prioritization")+ theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))
bar_eth_H
bar_eth_W <- ggplot(hv_eth_rev, aes(x=reorder(rownames(hv_eth_rev),-White), y=White))+geom_bar(stat="identity", fill="#F0E442")+xlab("Human values")+ylab("Mean")+ggtitle("White group human value prioritization")+ theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))
bar_eth_W
```

## Education level
 * Education level groups are created according to the below criteria
    + Less than high school group: early childhood education, primary education
    + High school education group: lower secondary, upper secondary
    + College education group: post-secondary non-tertiary, Short-cycle tertiary education 
    + Advanced degree group: bachelor's, master's, doctoral

```{r}
#Education level
hv_edu <- hv_analysis %>% filter(SchoolHighestEdu !="NA")
hv_edu <- hv_edu %>% filter(SchoolHighestEdu !="Prefer not to answer")
hv_edu <- hv_edu %>% mutate(Edu_g=ifelse(SchoolHighestEdu == c("Early childhood Education","Primary education"), "LessThanHighSchool",
        ifelse(SchoolHighestEdu == c("Upper secondary education", "Lower secondary education"),"HighSchoolEducation",
                      ifelse(SchoolHighestEdu == c("Post-secondary non-tertiary education", "Short-cycle tertiary education, e.g. vocational program"),"CollegeEducation", "AdvancedDegree"
                             ))))
hv_edu <- hv_edu %>%
  group_by(Edu_g) %>%
  summarise(ACHIEVEMENT = mean(ACHIEVEMENT_final_score, na.rm = TRUE), BENEVOLENCE = mean(BENEVOLENCE_final_score, na.rm = TRUE), CONFORMITY = mean(CONFORMITY_final_score, na.rm = TRUE), HEDONISM = mean(HEDONISM_final_score, na.rm = TRUE), POWER = mean(POWER_final_score, na.rm = TRUE), SECURITY = mean(SECURITY_final_score, na.rm = TRUE), SELF_DIRECTION = mean(`SELF DIRECTION_final_score`, na.rm = TRUE), STIMULATION = mean(STIMULATION_final_score, na.rm = TRUE), TRADITION = mean(TRADITION_final_score, na.rm = TRUE), UNIVERSALISM = mean(UNIVERSALISM_final_score, na.rm = TRUE))
hv_edu_rev <- t(hv_edu)
hv_edu_rev <- hv_edu_rev[-1,]
hv_edu_rev <- as.data.frame(hv_edu_rev)
colnames(hv_edu_rev) <- c("AdvancedDegree", "CollegeEducation", "HighSchoolEducation", "LessThanHighSchool")
hv_edu_rev$AdvancedDegree <- as.numeric(hv_edu_rev$AdvancedDegree)
hv_edu_rev$CollegeEducation <- as.numeric(hv_edu_rev$CollegeEducation)
hv_edu_rev$HighSchoolEducation <- as.numeric(hv_edu_rev$HighSchoolEducation)
hv_edu_rev$LessThanHighSchool <- as.numeric(hv_edu_rev$LessThanHighSchool)
```

 * Top 3 values of Less than high school: SELF-DIRECTION > SECURITY > ACHIEVEMENT 
 * Top 3 values of High school education: SELF-DIRECTION > ACHIEVEMENT > HEDONISM
 * Top 3 values of College education: ACHIEVEMENT > SELF-DIRECTION > SECURITY
 * Top 3 values of Advanced degree: ACHIEVEMENT > SECURITY > SELF-DIRECTION 
 * Values in lower ranks for all age groups: POWER/ TRADITION/ UNIVERSALISM
 
```{r}
#Education level count table
t_edu <- datatable(hv_edu %>%  
                     filter (Edu_g != "NA") %>%
                     group_by(Edu_g) %>% 
                     tally() %>% 
                     arrange(desc(n)) %>%
                     mutate(freq = round(n / sum(n),digits=2)))
t_edu
#Education bar graph
bar_edu_L <- ggplot(hv_edu_rev, aes(x=reorder(rownames(hv_edu_rev),-LessThanHighSchool), y=LessThanHighSchool))+geom_bar(stat="identity", fill="#CC79A7")+xlab("Human values")+ylab("Mean")+ggtitle("Less than high school education group human value prioritization")+ theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))
bar_edu_L
bar_edu_H <- ggplot(hv_edu_rev, aes(x=reorder(rownames(hv_edu_rev),-HighSchoolEducation), y=HighSchoolEducation))+geom_bar(stat="identity", fill="#D55E00")+xlab("Human values")+ylab("Mean")+ggtitle("High school education group human value prioritization")+ theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))
bar_edu_H
bar_edu_C <- ggplot(hv_edu_rev, aes(x=reorder(rownames(hv_edu_rev),-CollegeEducation), y=CollegeEducation))+geom_bar(stat="identity", fill="#0072B2")+xlab("Human values")+ylab("Mean")+ggtitle("College education group human value prioritization")+ theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))
bar_edu_C
bar_edu_A <- ggplot(hv_edu_rev, aes(x=reorder(rownames(hv_edu_rev),-AdvancedDegree), y=AdvancedDegree))+geom_bar(stat="identity", fill="#E69F00")+xlab("Human values")+ylab("Mean")+ggtitle("Advanced degree group human value prioritization")+ theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))
bar_edu_A

```

## Income level
 * Income level groups are created according to the below criteria
    + Low: less than $1,000-$2,999 
    + Middle: $3,000-$4,999
    + High: $5,000 or more

```{r}
hv_income <- hv_analysis %>% filter(Income !="NA")
hv_income <- hv_income %>% filter(Income !="Prefer not to answer")
hv_income <- hv_income %>% mutate(Income_g=ifelse(Income == c("Less than $1,000","$1,000 to $1,999","$2,000 to $2,999" ), "Low",
                                         ifelse(Income == c("$3,000 to $3,999", "$4,000 to $4,999"),"Middle","High")))
hv_income <- hv_income %>%
  group_by(Income_g) %>%
  summarise(ACHIEVEMENT = mean(ACHIEVEMENT_final_score, na.rm = TRUE), BENEVOLENCE = mean(BENEVOLENCE_final_score, na.rm = TRUE), CONFORMITY = mean(CONFORMITY_final_score, na.rm = TRUE), HEDONISM = mean(HEDONISM_final_score, na.rm = TRUE), POWER = mean(POWER_final_score, na.rm = TRUE), SECURITY = mean(SECURITY_final_score, na.rm = TRUE), SELF_DIRECTION = mean(`SELF DIRECTION_final_score`, na.rm = TRUE), STIMULATION = mean(STIMULATION_final_score, na.rm = TRUE), TRADITION = mean(TRADITION_final_score, na.rm = TRUE), UNIVERSALISM = mean(UNIVERSALISM_final_score, na.rm = TRUE))
hv_income_rev <- t(hv_income)
hv_income_rev <- hv_income_rev[-1,]
hv_income_rev <- as.data.frame(hv_income_rev)
colnames(hv_income_rev) <- c("High", "Low", "Middle")
hv_income_rev$High <- as.numeric(hv_income_rev$High)
hv_income_rev$Low <- as.numeric(hv_income_rev$Low)
hv_income_rev$Middle <- as.numeric(hv_income_rev$Middle)
```
 * Top 3 values of high income group: ACHIEVEMENT > SECURITY > SELF-DIRECTION 
 * Top 3 values of middle income group: SECURITY > ACHIEVEMENT > SELF-DIRECTION
 * Top 3 values of low income group: ACHIEVEMENT > SELF-DIRECTION > SECURITY
 * Values in lower ranks for all age groups: POWER < TRADITION < UNIVERSALISM
```{r}
#Income level count table
t_income <- datatable(hv_income %>%  
            filter (Income_g != "NA") %>%
            group_by(Income_g) %>% 
            tally() %>% 
            arrange(desc(n)) %>%
            mutate(freq = round(n / sum(n),digits=2)))
t_income
#Income bar graph
bar_income_H <- ggplot(hv_income_rev, aes(x=reorder(rownames(hv_income_rev),-High), y=High))+geom_bar(stat="identity", fill="lightblue")+xlab("Human values")+ylab("Mean")+ggtitle("High income group human value prioritization")+ theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))
bar_income_H
bar_income_M <- ggplot(hv_income_rev, aes(x=reorder(rownames(hv_income_rev),-Middle), y=Middle))+geom_bar(stat="identity", fill="lightgreen")+xlab("Human values")+ylab("Mean")+ggtitle("Middle income group human value prioritization")+ theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))
bar_income_M
bar_income_L <- ggplot(hv_income_rev, aes(x=reorder(rownames(hv_income_rev),-Low), y=Low))+geom_bar(stat="identity", fill="pink")+xlab("Human values")+ylab("Mean")+ggtitle("Low income group human value prioritization")+ theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))
bar_income_L

```

 
```{r}
```

# SEM (explain participation behaviors through human values)
  * Measurement model (observed variables-latent variables) & structural model (latent variables-latent variables)
  * Data cleaning (used mean score instead of final score. standardized variances are generated in the result instead)

```{r}

semdata <- hv_analysis[,c(13:40)]
semdata$StartContr <- na_interpolation(semdata$StartContr)
semdata$StartEnter <- na_interpolation(semdata$StartEnter)
semdata$StartInter <- na_interpolation(semdata$StartInter)
semdata$StartDist <- na_interpolation(semdata$StartDist)
semdata$StartSoc <- na_interpolation(semdata$StartSoc)
semdata$ContContr <- na_interpolation(semdata$ContContr)
semdata$ContEnter <- na_interpolation(semdata$ContEnter)
semdata$ContInter <- na_interpolation(semdata$ContInter)
semdata$ContDist <- na_interpolation(semdata$ContDist)
semdata$ContSoc <- na_interpolation(semdata$ContSoc)
semdata$ContLearn <- na_interpolation(semdata$ContLearn)
semdata$ContRep <- na_interpolation(semdata$ContRep)
semdata$StopTime <- na_interpolation(semdata$StopTime)
semdata$StopOtherOnlineAct <- na_interpolation(semdata$StopOtherOnlineAct)
semdata$StopOtherOfflineAct <- na_interpolation(semdata$StopOtherOfflineAct)
semdata$StopExpertise <- na_interpolation(semdata$StopExpertise)
semdata$StopPeople <- na_interpolation(semdata$StopPeople)
semdata$StopTask <- na_interpolation(semdata$StopTask)
semdata$HEDONISM_mean <- na_interpolation(semdata$HEDONISM_mean)
semdata$STIMULATION_mean <- na_interpolation(semdata$STIMULATION_mean)
semdata$`SELF DIRECTION_mean` <- na_interpolation(semdata$`SELF DIRECTION_mean`)
semdata$UNIVERSALISM_mean <- na_interpolation(semdata$UNIVERSALISM_mean)
semdata$BENEVOLENCE_mean <- na_interpolation(semdata$BENEVOLENCE_mean)
semdata$SECURITY_mean <- na_interpolation(semdata$SECURITY_mean)
semdata$TRADITION_mean <- na_interpolation(semdata$TRADITION_mean)
semdata$CONFORMITY_mean <- na_interpolation(semdata$CONFORMITY_mean)
semdata$ACHIEVEMENT_mean <- na_interpolation(semdata$ACHIEVEMENT_mean)
semdata$POWER_mean <- na_interpolation(semdata$POWER_mean)
names(semdata)[25] <- c("SELFDIRECTION_mean")
```

## Model 1 
 * exogenous indicators: mean value score of 10 human vales
 * exogenous latent variables: 4 human value dimensions
 * endogenous latent variables: start, continue, stop
 * endogenous indicators: survey questions asking about reasons to start, continue, and stop participation 
 
 * Goodness of fit test (model fit statistics): values do not reach threshold indicated in the parenthesis
    + p value > 0.05: 0.00 (Null hypothesis: this model fits)
    + SRMR < 0.08: 0.077 
    + TLI > 0.95: 0.577 
    + CFI > 0.95: 0.631
    + RMSEA < 0.06: 0.089

## Comparison between findings of previous work and those of our analysis 
 * Findings of previous work
    + Values related to initial participation: universalism, benevolence (self-transcendence), and security (conservation) 
    + Values related to continue participation: security
    + Values of which significant difference between the participants who remain and those who drop out of the project: security
  * Findings of analysis results
    + Values related to initial participation (partially true): conservation (1.45) / self-transcendence(-0.816)
    + Values related to continue participation (true): conservation (1.15)
    + Values of which significant difference between the participants who remain and those who drop out of the project (partially true): OTC (1.21) / security (0.922)
  * Additional findings - behavior survey questions which correspond to high loading (not necessarily align with human value and behavior)
    + Start: interest (0.67) > contribution (0.54) > entertainment (0.53)
    + Continue: interest (0.75) > contribution (0.61) > entertainment (0.60)
    + Stop: Offline activities (0.51) > online activities (0.48) > time (0.45)
    
  * Several issues
    + Warning message: covariance matrix of latent variables is not positive definite -> results should not be reported?dd
    + Judging from values of fit evaluation parameters, this model does not seem to have a good fit. Thus, the endogenous latent variables are split into separate models (model 2,3,4)

```{r}
#Modeling
#Model 1
#exogenous indicators: mean value score of 10 human values
#exogenous latent variables: 4 human value dimensions
#endogenous latent variables: start, continue, stop
#endogenous indicators: survey questions asking about reasons to start, continue, and stop participation
m1 <- 
'OTC =~ HEDONISM_mean + SELFDIRECTION_mean + STIMULATION_mean 
Conservation =~ SECURITY_mean + CONFORMITY_mean + TRADITION_mean 
Self_enhancement =~ ACHIEVEMENT_mean + POWER_mean
Self_transcendence =~ UNIVERSALISM_mean + BENEVOLENCE_mean

Start =~ StartEnter + StartInter + StartSoc + StartDist + StartContr
Continue =~ ContEnter + ContInter + ContSoc + ContLearn + ContRep + ContDist + ContContr
Stop =~ StopOtherOnlineAct + StopOtherOfflineAct + StopExpertise + StopPeople + StopTask + StopTime  

Start ~ OTC + Conservation + Self_enhancement + Self_transcendence
Continue ~ OTC + Conservation + Self_enhancement + Self_transcendence
Stop ~ OTC + Conservation + Self_enhancement + Self_transcendence'

fit1 <- sem(m1, data=semdata)
summary(fit1, standardized = TRUE, fit.measures=TRUE )
```

## Model 2 
 * exogenous indicators: mean value score of 10 human vales
 * exogenous latent variables: 4 human value dimensions
 * endogenous latent variables: start
 * endogenous indicators: survey questions asking about reasons to start participation
 
 * Goodness of fit test (model fit statistics): acceptable?
    + p value > 0.05: 0.00
    + SRMR < 0.08: 0.055 
    + TLI > 0.95: 0.817 
    + CFI > 0.95: 0.86
    + RMSEA < 0.06: 0.074 (acceptable < 0.08)

  * Loadings are slightly different, but findings of model 2,3,4 are same with those of model 1.
    
  * Several issues(same in model 2,3,4)
    + Same warning message: covariance matrix of latent variables is not positive definite -> results should not be reported?
    + Some regression loadings are larger than 1 (not sure if it's problematic)  

```{r}
sem_start <- semdata[,c(1:5,19:28)]
m2 <- 
  'OTC =~ HEDONISM_mean + SELFDIRECTION_mean + STIMULATION_mean 
Conservation =~ SECURITY_mean + CONFORMITY_mean + TRADITION_mean 
Self_enhancement =~ ACHIEVEMENT_mean + POWER_mean #factors less than 3 indicators can be problematic
Self_transcendence =~ UNIVERSALISM_mean + BENEVOLENCE_mean

Start =~ StartEnter + StartInter + StartSoc + StartDist + StartContr

Start ~ OTC + Conservation + Self_enhancement + Self_transcendence
'

fit2 <- sem(m2, data=sem_start)
summary(fit2, standardized = TRUE, fit.measures=TRUE )
diagram2<-semPlot::semPaths(fit2,
                           rotation = 4,
                           whatLabels="std", intercepts=FALSE,                      
                           curveAdjacent = TRUE, title=TRUE,
                           layout="tree",curvePivot=TRUE,
                           edge.color = "black",
                           edge.label.cex=.9,
                           edge.label.position=0.7
)
```

## Model 3 
 * exogenous indicators: mean value score of 10 human vales
 * exogenous latent variables: 4 human value dimensions
 * endogenous latent variables: continue
 * endogenous indicators: survey questions asking about reasons to continue participation
 
 * Goodness of fit test (model fit statistics): acceptable?
    + p value > 0.05: 0.00
    + SRMR < 0.08: 0.067 
    + TLI > 0.95: 0.822 
    + CFI > 0.95: 0.778
    + RMSEA < 0.06: 0.078
    
```{r}
sem_continue <- semdata[,c(6:12,19:28)]
m3 <- 
  'OTC =~ HEDONISM_mean + SELFDIRECTION_mean + STIMULATION_mean 
Conservation =~ SECURITY_mean + CONFORMITY_mean + TRADITION_mean 
Self_enhancement =~ ACHIEVEMENT_mean + POWER_mean
Self_transcendence =~ UNIVERSALISM_mean + BENEVOLENCE_mean

Continue =~ ContEnter + ContInter + ContSoc + ContLearn + ContRep + ContDist + ContContr

Continue ~ OTC + Conservation + Self_enhancement + Self_transcendence
'
fit3 <- sem(m3, data=sem_continue)
summary(fit3, standardized = TRUE, fit.measures=TRUE )
diagram3<-semPlot::semPaths(fit3,
                           rotation = 4,
                           whatLabels="std", intercepts=FALSE,                      
                           curveAdjacent = TRUE, title=TRUE,
                           layout="tree",curvePivot=TRUE,
                           edge.color = "black",
                           edge.label.cex=.9,
                           edge.label.position=0.7
)
```

## Model 4 
 * exogenous indicators: mean value score of 10 human vales
 * exogenous latent variables: 4 human value dimensions
 * endogenous latent variables: stop
 * endogenous indicators: survey questions asking about reasons to stop participation
 
 * Goodness of fit test (model fit statistics): acceptable?
    + p value > 0.05: 0.00
    + SRMR < 0.08: 0.051 
    + TLI > 0.95: 0.797 
    + CFI > 0.95: 0.841
    + RMSEA < 0.06: 0.072

```{r}
sem_stop <- semdata[,c(13:18,19:28)]
m4 <- 
  'OTC =~ HEDONISM_mean + SELFDIRECTION_mean + STIMULATION_mean 
Conservation =~ SECURITY_mean + CONFORMITY_mean + TRADITION_mean 
Self_enhancement =~ ACHIEVEMENT_mean + POWER_mean
Self_transcendence =~ UNIVERSALISM_mean + BENEVOLENCE_mean

Stop =~ StopOtherOnlineAct + StopOtherOfflineAct + StopExpertise + StopPeople + StopTask + StopTime  

Stop ~ OTC + Conservation + Self_enhancement + Self_transcendence
'
fit4 <- sem(m4, data=sem_stop)
summary(fit4, standardized = TRUE, fit.measures=TRUE )
diagram4<-semPlot::semPaths(fit4,
                            rotation = 4,
                            whatLabels="std", intercepts=FALSE,                      
                            curveAdjacent = TRUE, title=TRUE,
                            layout="tree",curvePivot=TRUE,
                            edge.color = "black",
                            edge.label.cex=.9,
                            edge.label.position=0.7
)
```

