---
title: "Human value analysis_ver4"
author: "Ellie Jeong and Corey Jackson"
date: "`r Sys.time()`"
output:
  html_document:
    fig_caption: yes
    highlight: pygments
    number_sections: yes
    theme: spacelab
    toc: yes
    toc_float:
      smooth_scroll: no
  pdf_document:
    toc: yes
    toc_depth: '5'
always_allow_html: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA,  warning = FALSE, message = FALSE)
```

```{r echo=FALSE}
# load packages and data
library(readr)
library(dplyr)
library(DT)
library(tidytext)
library(forcats)
library(ggplot2)
library(lubridate)
library(readr)
library(data.table)
library(tidytext)
library(entropy)
library(reshape2)
library(scales)
library(dplyr)
library(tm)
library(rapport)
library(knitr)
library(kableExtra)
library(corpus)
library(cowplot)
library(gridExtra)
library(caret)
library(reshape2)
library(ltm)
library(psych)
library(ggsci)
library(rcompanion)
library(pROC)
library(ngram)
library(urltools)
library(tidyverse)
library(readxl)
library(trend)
library(data.table)
library(DT)
library(ggsci)
library(HH)
library(cluster)
library(factoextra)
library(imputeTS)
library(corrplot)
library(foreign) 
library(lavaan)
library(semPlot)
library(agricolae)

#setwd("C:/Users/hp/Box/Zoo Engagement Survey Pt 2/Data/Human Values Research [Ellie]/Analysis (rmd, html)")

#hv_analysis <- read_csv("values_analysis.csv")
hv_analysis <- read_csv("/Volumes/cbjackson2/usersurvey/values_analysis.csv") # Imported from cleaned data

```

# Reliability analysis

```{r }
#completed_responses <- read_csv("completed_responses.csv") # Imported from cleaned data
completed_responses <- read_csv("/Volumes/cbjackson2/usersurvey/complete_responses.csv") # Imported from cleaned data

```

```{r pvq_setup, include=FALSE,cache=FALSE}
pvq <- completed_responses[,c(10,91:111)]
pvq <- pvq[complete.cases(pvq), ] 

BENEVOLENCE <- c("Q60_7","Q60_6")
UNIVERSALISM <- c("Q60_3","Q60_4","Q60_5")
SELF_DIRECTION <- c("Q60_2","Q60_1")
STIMULATION <- c("Q60_13","Q60_12")
HEDONISM <- c("Q60_15","Q60_14")
ACHIEVEMENT <- c("Q60_17","Q60_16")
POWER <- c("Q60_18","Q60_19")
SECURITY <- c("Q60_21","Q60_20")
CONFORMITY <- c("Q60_10","Q60_11")
TRADITION <- c("Q60_9","Q60_8")

SelfTranscendence <- c(BENEVOLENCE,UNIVERSALISM)
SelfEnhancement  <- c(ACHIEVEMENT,POWER,HEDONISM)
Opennesstochange <- c(SELF_DIRECTION,STIMULATION)
Conservation <- c(SECURITY,CONFORMITY,TRADITION)

pvq.m <- melt(pvq, id.vars = "ResponseId")
pvq.m$OVs <- ifelse(pvq.m$variable %in% BENEVOLENCE,"BENEVOLENCE",
             ifelse(pvq.m$variable %in% UNIVERSALISM,"UNIVERSALISM",
             ifelse(pvq.m$variable %in% SELF_DIRECTION,"SELF DIRECTION",
             ifelse(pvq.m$variable %in% STIMULATION,"STIMULATION",
             ifelse(pvq.m$variable %in% HEDONISM,"HEDONISM",
             ifelse(pvq.m$variable %in% ACHIEVEMENT,"ACHIEVEMENT",
             ifelse(pvq.m$variable %in% POWER,"POWER",
             ifelse(pvq.m$variable %in% SECURITY,"SECURITY",
             ifelse(pvq.m$variable %in% CONFORMITY,"CONFORMITY",
             ifelse(pvq.m$variable %in% TRADITION,"TRADITION",NA
                ))))))))))
pvq.m$score <- as.numeric(substring(pvq.m$value, 1, 1))

# cast data for reliability high order
pvq.reliability <- pvq.m %>%
    dcast(ResponseId ~ variable, value.var = "score") 

st.reliability <- pvq.reliability[which(names(pvq.reliability) %in% SelfTranscendence)] # capture items for HO constructs
se.reliability <- pvq.reliability[which(names(pvq.reliability) %in% SelfEnhancement)]
otc.reliability <- pvq.reliability[which(names(pvq.reliability) %in% Opennesstochange)]
c.reliability <- pvq.reliability[which(names(pvq.reliability) %in% Conservation)]

pvq.users <- pvq.m %>% 
  group_by(ResponseId) %>%  
  summarize(
    mrat = mean(score)
  )

pvq.users.values <- pvq.m %>% 
  group_by(ResponseId,OVs) %>%  
  summarize(
    score = mean(score)
  )

pvq.values <- pvq.m %>% 
  group_by(OVs) %>%  
  summarize(
    score = mean(score)
    )

pvq.values <- pvq.m %>% 
  group_by(OVs) %>%  
  summarize(
    score = sd(score)
    )

#col=c("#E94E1B", "#F7AA4E", "#BEBEBE", "#6193CE", "#00508C")
pvq.users.values <- merge(pvq.users.values,pvq.users, by=c("ResponseId"))
pvq.users.values$final_score <- pvq.users.values$score - pvq.users.values$mrat

pvq.values.viz <- ggplot(pvq.users.values, aes(x = reorder(OVs, -score), y=score)) + 
     geom_violin(trim=FALSE)  + coord_flip() + theme_minimal() + labs(x="PVQ Category",y="Mean Score") +  theme(legend.position="none",legend.text = element_text(size=7),legend.key.size = unit(.5,"line")) +       
   #scale_fill_brewer(palette="PRGn")
   scale_fill_aaas()  + theme(complete = F) 


pvq.values.viz <- pvq.values.viz + stat_summary(fun.data=mean_sdl, 
                 geom="pointrange", color="#00508C")
                 # + scale_color_manual(values=c("#999999", "#E69F00", "#56B4E9"))


hopvq.m <- melt(pvq, id.vars = "ResponseId")

hopvq.m$OVs <- ifelse(hopvq.m$variable %in% SelfTranscendence,"Self-Transcendence",
             ifelse(hopvq.m$variable %in% SelfEnhancement,"Self-Enhancement",
             ifelse(hopvq.m$variable %in% Opennesstochange,"Openness to change",
             ifelse(hopvq.m$variable %in% Conservation,"Conservation",NA
                ))))
hopvq.m$score <- as.numeric(substring(hopvq.m$value, 1, 1))


hopvq.users <- hopvq.m %>% 
  group_by(ResponseId) %>%  
  summarize(
    mrat = mean(score)
  )

hopvq.users.values <- hopvq.m %>% 
  group_by(ResponseId,OVs) %>%  
  summarize(
    score = mean(score)
  )

hopvq.values <- hopvq.m %>% 
  group_by(OVs) %>%  
  summarize(
    score = mean(score)
    )

hopvq.values <- hopvq.m %>% 
  group_by(OVs) %>%  
  summarize(
    score = sd(score)
    )


#col=c("#E94E1B", "#F7AA4E", "#BEBEBE", "#6193CE", "#00508C")

hopvq.users.values <- merge(hopvq.users.values,hopvq.users, by=c("ResponseId"))
hopvq.users.values$final_score <- hopvq.users.values$score - hopvq.users.values$mrat

 hopvq.values.viz <- ggplot(hopvq.users.values, aes(x = reorder(OVs, -score), y=score)) + 
     geom_violin(trim=FALSE)  + coord_flip() + theme_minimal() + labs(x="PVQ Category",y="Mean Score") +  theme(legend.position="none",legend.text = element_text(size=7),legend.key.size = unit(.5,"line")) +       
   #scale_fill_brewer(palette="PRGn")
   scale_fill_aaas()  + theme(complete = F) 

hopvq.values.viz <- hopvq.values.viz + stat_summary(fun.data=mean_sdl, 
                 geom="pointrange", color="#00508C")
                 # + scale_color_manual(values=c("#999999", "#E69F00", "#56B4E9"))
```

Literature on the PVQ 
  - [A Proposal for Measuring Value Orientations across Nations ](https://www.europeansocialsurvey.org/docs/methodology/core_ess_questionnaire/ESS_core_questionnaire_human_values.pdf)
  
  **Q: Below are some statements that describe a person. Read them carefully and respond to how each statement resonates with you as a person. Rate your responses on a scale of 1-6, where ‘1’ means ‘very much like me,’ and ‘6’ implies ‘not at all like me.**

## Method


## Results for the Portrait Values Questionnaire (PVQ)

```{r}
datatable(pvq.users.values[1:40,])
```

### Reliability analysis


#### Reliability for self-transcendence
```{r}
psych::alpha(st.reliability)
```

#### Reliability for self- enhancement
```{r}
psych::alpha(se.reliability)
```

#### Reliability for openness to change

```{r}
psych::alpha(otc.reliability)
```

#### Reliability for conservativeness
```{r}
psych::alpha(c.reliability)
```

### PVQ Results
```{r}
pvq.values.viz
```

```{r}
hopvq.values.viz
```

# Human value prioritization: Descriptive statistics

Prioritize 10 Human Values of different demographic groups (gender/age/ethnicity/education level/income level)

## Gender

```{r pressure3}
hv_gender <- hv_analysis %>%
  group_by(Gender_Select) %>%
  summarise(ACHIEVEMENT = mean(ACHIEVEMENT_mean, na.rm = TRUE), 
            BENEVOLENCE = mean(BENEVOLENCE_mean, na.rm = TRUE), 
            CONFORMITY = mean(CONFORMITY_mean, na.rm = TRUE), 
            HEDONISM = mean(HEDONISM_mean, na.rm = TRUE), 
            POWER = mean(POWER_mean, na.rm = TRUE), 
            SECURITY = mean(SECURITY_mean, na.rm = TRUE), 
            SELF_DIRECTION = mean(`SELF DIRECTION_mean`, na.rm = TRUE), 
            STIMULATION = mean(STIMULATION_mean, na.rm = TRUE), 
            TRADITION = mean(TRADITION_mean, na.rm = TRUE), 
            UNIVERSALISM = mean(UNIVERSALISM_mean, na.rm = TRUE))


hv_gender <- as.data.frame(hv_gender)
hv_gender_rev <- t(hv_gender)
hv_gender_rev <- hv_gender_rev[-1,]
hv_gender_rev <- hv_gender_rev[,c(1,2)]
colnames(hv_gender_rev) <- c("Female", "Male")
hv_gender_rev <- as.data.frame(hv_gender_rev)
hv_gender_rev$Female <- as.numeric(hv_gender_rev$Female)
hv_gender_rev$Male <- as.numeric(hv_gender_rev$Male)
```
 * Top 3 values of female group: ACHIEVEMENT > SELF-DIRECTION > SECURITY
 * Top 3 values of male group: ACHIEVEMENT > SECURITY > SELF-DIRECTION 
 * Values in lower ranks for both groups: POWER < TRADITION < UNIVERSALISM
```{r pressure2}
#Gender count table
t_gender <- datatable(hv_analysis %>%  
                        filter (Gender_Select != "NA") %>%
                        group_by(Gender_Select) %>% 
                        tally() %>% 
                        arrange(desc(n)) %>%
                        mutate(freq = round(n / sum(n),digits=2)))
t_gender
#Gender bar graph
bar_gender_F <- ggplot(hv_gender_rev, aes(x=reorder(rownames(hv_gender_rev),-Female), y=Female))+geom_bar(stat="identity", fill="red")+xlab("Human values")+ylab("Mean")+ggtitle("Female human value prioritization") + theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))  
bar_gender_F
bar_gender_M <- ggplot(hv_gender_rev, aes(x=reorder(rownames(hv_gender_rev),-Male), y=Male))+geom_bar(stat="identity", fill="blue")+xlab("Human values")+ylab("Mean")+ggtitle("Male human value prioritization")+ theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))
bar_gender_M
```

## Age
 * Age groups are created according to the below criteria
    + Young: 18~39
    + Middle-aged: 40~65
    + Old: 66~99
 
```{r}
#Age
hv_age <- hv_analysis %>% 
  mutate(Age_g=ifelse(Age<40, "Young", 
                        ifelse(Age<66, "Middle", "Old")))
hv_age2 <- hv_age %>%
  group_by(Age_g) %>%
   summarise(ACHIEVEMENT = mean(ACHIEVEMENT_mean, na.rm = TRUE), 
            BENEVOLENCE = mean(BENEVOLENCE_mean, na.rm = TRUE), 
            CONFORMITY = mean(CONFORMITY_mean, na.rm = TRUE), 
            HEDONISM = mean(HEDONISM_mean, na.rm = TRUE), 
            POWER = mean(POWER_mean, na.rm = TRUE), 
            SECURITY = mean(SECURITY_mean, na.rm = TRUE), 
            SELF_DIRECTION = mean(`SELF DIRECTION_mean`, na.rm = TRUE), 
            STIMULATION = mean(STIMULATION_mean, na.rm = TRUE), 
            TRADITION = mean(TRADITION_mean, na.rm = TRUE), 
            UNIVERSALISM = mean(UNIVERSALISM_mean, na.rm = TRUE))%>% 
  filter(Age_g != "NA")
hv_age_rev <- t(hv_age2)
hv_age_rev <- hv_age_rev[-1,]
colnames(hv_age_rev) <- c("Middle", "Old", "Young")
hv_age_rev <- as.data.frame(hv_age_rev)
hv_age_rev$Middle <- as.numeric(hv_age_rev$Middle)
hv_age_rev$Old <- as.numeric(hv_age_rev$Old)
hv_age_rev$Young <- as.numeric(hv_age_rev$Young)

hv_all <- merge(hv_age_rev,hv_gender_rev, by='row.names', all = TRUE)
```
 * Top 3 values of young people: ACHIEVEMENT > SECURITY > SELF-DIRECTION 
 * Top 3 values of middle-aged people: ACHIEVEMENT > SELF-DIRECTION > SECURITY
 * Top 3 values of old people: ACHIEVEMENT > SELF-DIRECTION > SECURITY
 * Values in lower ranks for all age groups: POWER < TRADITION < UNIVERSALISM
```{r}
#Age count table
t_age <- datatable(hv_age %>%  
                     filter (Age_g != "NA") %>%
                     group_by(Age_g) %>% 
                     tally() %>% 
                     arrange(desc(n)) %>%
                     mutate(freq = round(n / sum(n),digits=2)))
t_age
#Age bar graph
bar_age_Y <- ggplot(hv_age_rev, aes(x=reorder(rownames(hv_age_rev),-Young), y=Young))+geom_bar(stat="identity", fill="#D55E00")+xlab("Human values")+ylab("Mean")+ggtitle("Young group human value prioritization")+ theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))
bar_age_Y
bar_age_M <- ggplot(hv_age_rev, aes(x=reorder(rownames(hv_age_rev),-Middle), y=Middle))+geom_bar(stat="identity", fill="#0072B2")+xlab("Human values")+ylab("Mean")+ggtitle("Middle-aged group human value prioritization")+ theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))
bar_age_M
bar_age_O <- ggplot(hv_age_rev, aes(x=reorder(rownames(hv_age_rev),-Old), y=Old))+geom_bar(stat="identity", fill="#CC79A7")+xlab("Human values")+ylab("Mean")+ggtitle("Old group human value prioritization")+ theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))
bar_age_O
```

## Ethnicity

```{r}
hv_eth <- hv_analysis %>% filter(Ethnicity_Select %in% c("White (A person having origins in any of the original peoples of Europe, the Middle East, or North Africa.)","Asian (A person having origins in any of the original peoples of the Far East, Southeast Asia, or the Indian subcontinent)","Black (A person having origins in any of the black racial groups of Africa.)","Hispanic/Latino/Spanish origin (A person of Cuban, Mexican, Puerto Rican, South or Central American, or other Spanish culture or origin, regardless of race)") )
hv_eth2 <- hv_eth %>%
  group_by(Ethnicity_Select) %>%
   summarise(ACHIEVEMENT = mean(ACHIEVEMENT_mean, na.rm = TRUE), 
            BENEVOLENCE = mean(BENEVOLENCE_mean, na.rm = TRUE), 
            CONFORMITY = mean(CONFORMITY_mean, na.rm = TRUE), 
            HEDONISM = mean(HEDONISM_mean, na.rm = TRUE), 
            POWER = mean(POWER_mean, na.rm = TRUE), 
            SECURITY = mean(SECURITY_mean, na.rm = TRUE), 
            SELF_DIRECTION = mean(`SELF DIRECTION_mean`, na.rm = TRUE), 
            STIMULATION = mean(STIMULATION_mean, na.rm = TRUE), 
            TRADITION = mean(TRADITION_mean, na.rm = TRUE), 
            UNIVERSALISM = mean(UNIVERSALISM_mean, na.rm = TRUE))

hv_eth_rev <- t(hv_eth2)
hv_eth_rev <- hv_eth_rev[-1,]
hv_eth_rev <- as.data.frame(hv_eth_rev)
colnames(hv_eth_rev) <- c("Asian", "Black", "Hispanic", "White")
hv_eth_rev$Asian <- as.numeric(hv_eth_rev$Asian)
hv_eth_rev$Black <- as.numeric(hv_eth_rev$Black)
hv_eth_rev$Hispanic <- as.numeric(hv_eth_rev$Hispanic)
hv_eth_rev$White <- as.numeric(hv_eth_rev$White)


```
 * Top 3 values of Asian: ACHIEVEMENT > SECURITY > SELF-DIRECTION 
 * Top 3 values of Black: ACHIEVEMENT > BENEVOLENCE > SECURITY
 * Top 3 values of Hispanic/Latino/Spanish origin: ACHIEVEMENT > SELF-DIRECTION > SECURITY
 * Top 3 values of White: ACHIEVEMENT > SECURITY > SELF-DIRECTION
 * Values in lower ranks for all age groups: POWER < TRADITION < UNIVERSALISM
```{r}
#Ethnicity count table
t_eth <- datatable(hv_analysis %>%  
                     filter (Ethnicity_Select %in% c("White (A person having origins in any of the original peoples of Europe, the Middle East, or North Africa.)","Asian (A person having origins in any of the original peoples of the Far East, Southeast Asia, or the Indian subcontinent)","Black (A person having origins in any of the black racial groups of Africa.)","Hispanic/Latino/Spanish origin (A person of Cuban, Mexican, Puerto Rican, South or Central American, or other Spanish culture or origin, regardless of race)") ) %>%
                     group_by(Ethnicity_Select) %>% 
                     tally() %>% 
                     arrange(desc(n)) %>%
                     mutate(freq = round(n / sum(n),digits=2)))
t_eth
#Ethnicity bar graph
bar_eth_A <- ggplot(hv_eth_rev, aes(x=reorder(rownames(hv_eth_rev),-Asian), y=Asian))+geom_bar(stat="identity", fill="#E69F00")+xlab("Human values")+ylab("Mean")+ggtitle("Asian group human value prioritization")+ theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))
bar_eth_A
bar_eth_B <- ggplot(hv_eth_rev, aes(x=reorder(rownames(hv_eth_rev),-Black), y=Black))+geom_bar(stat="identity", fill="#56B4E9")+xlab("Human values")+ylab("Mean")+ggtitle("Black group human value prioritization")+ theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))
bar_eth_B
bar_eth_H <- ggplot(hv_eth_rev, aes(x=reorder(rownames(hv_eth_rev),-Hispanic), y=Hispanic))+geom_bar(stat="identity", fill="#009E73")+xlab("Human values")+ylab("Mean")+ggtitle("Hispanic group human value prioritization")+ theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))
bar_eth_H
bar_eth_W <- ggplot(hv_eth_rev, aes(x=reorder(rownames(hv_eth_rev),-White), y=White))+geom_bar(stat="identity", fill="#F0E442")+xlab("Human values")+ylab("Mean")+ggtitle("White group human value prioritization")+ theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))
bar_eth_W
```

## Education level
 * Education level groups are created according to the below criteria
    + Less than high school group: early childhood education, primary education
    + High school education group: lower secondary, upper secondary
    + College education group: post-secondary non-tertiary, Short-cycle tertiary education 
    + Advanced degree group: bachelor's, master's, doctoral

```{r}
#Education level
hv_edu <- hv_analysis %>% filter(SchoolHighestEdu !="NA")
hv_edu <- hv_edu %>% filter(SchoolHighestEdu !="Prefer not to answer")
hv_edu <- hv_edu %>% mutate(Edu_g=ifelse(SchoolHighestEdu == c("Early childhood Education","Primary education"), "LessThanHighSchool",
        ifelse(SchoolHighestEdu == c("Upper secondary education", "Lower secondary education"),"HighSchoolEducation",
                      ifelse(SchoolHighestEdu == c("Post-secondary non-tertiary education", "Short-cycle tertiary education, e.g. vocational program"),"CollegeEducation", "AdvancedDegree"
                             ))))

hv_edu2 <- hv_edu %>%
  group_by(Edu_g) %>%
   summarise(ACHIEVEMENT = mean(ACHIEVEMENT_mean, na.rm = TRUE), 
            BENEVOLENCE = mean(BENEVOLENCE_mean, na.rm = TRUE), 
            CONFORMITY = mean(CONFORMITY_mean, na.rm = TRUE), 
            HEDONISM = mean(HEDONISM_mean, na.rm = TRUE), 
            POWER = mean(POWER_mean, na.rm = TRUE), 
            SECURITY = mean(SECURITY_mean, na.rm = TRUE), 
            SELF_DIRECTION = mean(`SELF DIRECTION_mean`, na.rm = TRUE), 
            STIMULATION = mean(STIMULATION_mean, na.rm = TRUE), 
            TRADITION = mean(TRADITION_mean, na.rm = TRUE), 
            UNIVERSALISM = mean(UNIVERSALISM_mean, na.rm = TRUE))

hv_edu_rev <- t(hv_edu2)
hv_edu_rev <- hv_edu_rev[-1,]
hv_edu_rev <- as.data.frame(hv_edu_rev)
colnames(hv_edu_rev) <- c("AdvancedDegree", "CollegeEducation", "HighSchoolEducation", "LessThanHighSchool")
hv_edu_rev$AdvancedDegree <- as.numeric(hv_edu_rev$AdvancedDegree)
hv_edu_rev$CollegeEducation <- as.numeric(hv_edu_rev$CollegeEducation)
hv_edu_rev$HighSchoolEducation <- as.numeric(hv_edu_rev$HighSchoolEducation)
hv_edu_rev$LessThanHighSchool <- as.numeric(hv_edu_rev$LessThanHighSchool)

hv_all2 <- merge(hv_eth_rev,hv_edu_rev, by='row.names', all = TRUE)

```

 * Top 3 values of Less than high school: SELF-DIRECTION > SECURITY > ACHIEVEMENT 
 * Top 3 values of High school education: SELF-DIRECTION > ACHIEVEMENT > HEDONISM
 * Top 3 values of College education: ACHIEVEMENT > SELF-DIRECTION > SECURITY
 * Top 3 values of Advanced degree: ACHIEVEMENT > SECURITY > SELF-DIRECTION 
 * Values in lower ranks for all age groups: POWER/ TRADITION/ UNIVERSALISM
 
```{r}
#Education level count table
t_edu <- datatable(hv_edu %>%  
                     filter (Edu_g != "NA") %>%
                     group_by(Edu_g) %>% 
                     tally() %>% 
                     arrange(desc(n)) %>%
                     mutate(freq = round(n / sum(n),digits=2)))
t_edu
#Education bar graph
bar_edu_L <- ggplot(hv_edu_rev, aes(x=reorder(rownames(hv_edu_rev),-LessThanHighSchool), y=LessThanHighSchool))+geom_bar(stat="identity", fill="#CC79A7")+xlab("Human values")+ylab("Mean")+ggtitle("Less than high school education group human value prioritization")+ theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))
bar_edu_L
bar_edu_H <- ggplot(hv_edu_rev, aes(x=reorder(rownames(hv_edu_rev),-HighSchoolEducation), y=HighSchoolEducation))+geom_bar(stat="identity", fill="#D55E00")+xlab("Human values")+ylab("Mean")+ggtitle("High school education group human value prioritization")+ theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))
bar_edu_H
bar_edu_C <- ggplot(hv_edu_rev, aes(x=reorder(rownames(hv_edu_rev),-CollegeEducation), y=CollegeEducation))+geom_bar(stat="identity", fill="#0072B2")+xlab("Human values")+ylab("Mean")+ggtitle("College education group human value prioritization")+ theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))
bar_edu_C
bar_edu_A <- ggplot(hv_edu_rev, aes(x=reorder(rownames(hv_edu_rev),-AdvancedDegree), y=AdvancedDegree))+geom_bar(stat="identity", fill="#E69F00")+xlab("Human values")+ylab("Mean")+ggtitle("Advanced degree group human value prioritization")+ theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))
bar_edu_A

```

## Income level
 * Income level groups are created according to the below criteria
    + Low: less than $1,000-$2,999 
    + Middle: $3,000-$4,999
    + High: $5,000 or more

```{r}
hv_income <- hv_analysis %>% filter(Income !="NA")
hv_income <- hv_income %>% filter(Income !="Prefer not to answer")
hv_income <- hv_income %>% mutate(Income_g=ifelse(Income == c("Less than $1,000","$1,000 to $1,999","$2,000 to $2,999" ), "Low",
                                         ifelse(Income == c("$3,000 to $3,999", "$4,000 to $4,999"),"Middle","High")))
```
 * Top 3 values of high income group: ACHIEVEMENT > SECURITY > SELF-DIRECTION 
 * Top 3 values of middle income group: SECURITY > ACHIEVEMENT > SELF-DIRECTION
 * Top 3 values of low income group: ACHIEVEMENT > SELF-DIRECTION > SECURITY
 * Values in lower ranks for all age groups: POWER < TRADITION < UNIVERSALISM
```{r}
#Income level count table
hv_income2 <- hv_income %>%
  group_by(Income_g) %>%
   summarise(ACHIEVEMENT = mean(ACHIEVEMENT_mean, na.rm = TRUE), 
            BENEVOLENCE = mean(BENEVOLENCE_mean, na.rm = TRUE), 
            CONFORMITY = mean(CONFORMITY_mean, na.rm = TRUE), 
            HEDONISM = mean(HEDONISM_mean, na.rm = TRUE), 
            POWER = mean(POWER_mean, na.rm = TRUE), 
            SECURITY = mean(SECURITY_mean, na.rm = TRUE), 
            SELF_DIRECTION = mean(`SELF DIRECTION_mean`, na.rm = TRUE), 
            STIMULATION = mean(STIMULATION_mean, na.rm = TRUE), 
            TRADITION = mean(TRADITION_mean, na.rm = TRUE), 
            UNIVERSALISM = mean(UNIVERSALISM_mean, na.rm = TRUE))

hv_income_rev <- t(hv_income2)
hv_income_rev <- hv_income_rev[-1,]
hv_income_rev <- as.data.frame(hv_income_rev)
colnames(hv_income_rev) <- c("High", "Low", "Middle")
hv_income_rev$High <- as.numeric(hv_income_rev$High)
hv_income_rev$Low <- as.numeric(hv_income_rev$Low)
hv_income_rev$Middle <- as.numeric(hv_income_rev$Middle)
t_income <- datatable(hv_income %>%  
            filter (Income_g != "NA") %>%
            group_by(Income_g) %>% 
            tally() %>% 
            arrange(desc(n)) %>%
            mutate(freq = round(n / sum(n),digits=2)))
t_income

#Income bar graph
bar_income_H <- ggplot(hv_income_rev, aes(x=reorder(rownames(hv_income_rev),-High), y=High))+geom_bar(stat="identity", fill="lightblue")+xlab("Human values")+ylab("Mean")+ggtitle("High income group human value prioritization")+ theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))
bar_income_H
bar_income_M <- ggplot(hv_income_rev, aes(x=reorder(rownames(hv_income_rev),-Middle), y=Middle))+geom_bar(stat="identity", fill="lightgreen")+xlab("Human values")+ylab("Mean")+ggtitle("Middle income group human value prioritization")+ theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))
bar_income_M
bar_income_L <- ggplot(hv_income_rev, aes(x=reorder(rownames(hv_income_rev),-Low), y=Low))+geom_bar(stat="identity", fill="pink")+xlab("Human values")+ylab("Mean")+ggtitle("Low income group human value prioritization")+ theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5 ))
bar_income_L

names(hv_all)[1] <- "value"
names(hv_all2)[1] <- "value"

hv_income_rev$value <- rownames(hv_income_rev)

hv_all <- merge(hv_all,hv_all2, by = "value")
hv_all <- merge(hv_all,hv_income_rev, by = "value")
```

# ANOVA & TukeyHSD test 
 * ANOVA: When there are three or more independent groups, we apply a one-way ANOVA to see if there is a significant difference.The p-value for one-way ANOVA is less than 0.05 indicate that at least one of the treatment groups differs from the others.

 * TukeyHSD test: The Tukey HSD test is a post hoc multiple comparison test which allows for all possible pairwise comparisons while keeping the family-wise error rate low. P-value less than 0.05 means the difference between the pairs is statistically significant.
 
## Gender: there are only two independent groups (male, female). Thus, this variable cannot be tested using one-way ANOVA model

## Age
 * ANOVA & TukeyHSD test: All values are influenced by age
 
```{r}
# Data cleaning 
hv_mean2 <- hv_age[,c(2,4,6,7,10,12,13:40,61)]
names(hv_mean2)[25:35] <- c("ACHIEVEMENT", "BENEVOLENCE", "CONFORMITY", "HEDONISM", "POWER", "SECURITY", "SELF_DIRECTION", "STIMULATION", "TRADITION", "UNIVERSALISM", "group")
hv_complete_a2 <- complete.cases(hv_mean2[, 1:35])
hv_final_age <- hv_mean2[hv_complete_a2, 1:35]

# ANOVA analysis
anova_age_hed <- aov(HEDONISM ~ group, data = hv_final_age)
summary(anova_age_hed)
anova_age_sel <- aov(SELF_DIRECTION ~ group, data = hv_final_age)
summary(anova_age_sel)
anova_age_sti <- aov(STIMULATION ~ group, data = hv_final_age)
summary(anova_age_sti)
anova_age_sec <- aov(SECURITY ~ group, data = hv_final_age)
summary(anova_age_sec)
anova_age_con <- aov(CONFORMITY ~ group, data = hv_final_age)
summary(anova_age_con)
anova_age_tra <- aov(TRADITION ~ group, data = hv_final_age)
summary(anova_age_tra)
anova_age_ach <- aov(ACHIEVEMENT ~ group, data = hv_final_age)
summary(anova_age_ach)
anova_age_pow <- aov(POWER ~ group, data = hv_final_age)
summary(anova_age_pow)
anova_age_uni <- aov(UNIVERSALISM ~ group, data = hv_final_age)
summary(anova_age_uni)
anova_age_ben <- aov(BENEVOLENCE ~ group, data = hv_final_age)
summary(anova_age_ben)

#TukeyHSD test
TukeyHSD(anova_age_hed,conf.level=.95)
plot(TukeyHSD(anova_age_hed, conf.level=.95), las = 2)
TukeyHSD(anova_age_sel,conf.level=.95)
plot(TukeyHSD(anova_age_sel, conf.level=.95), las = 2)
TukeyHSD(anova_age_sti,conf.level=.95)
plot(TukeyHSD(anova_age_sti, conf.level=.95), las = 2)
TukeyHSD(anova_age_sec,conf.level=.95)
plot(TukeyHSD(anova_age_sec, conf.level=.95), las = 2)
TukeyHSD(anova_age_con,conf.level=.95)
plot(TukeyHSD(anova_age_con, conf.level=.95), las = 2)
TukeyHSD(anova_age_tra,conf.level=.95)
plot(TukeyHSD(anova_age_tra, conf.level=.95), las = 2)
TukeyHSD(anova_age_ach,conf.level=.95)
plot(TukeyHSD(anova_age_ach, conf.level=.95), las = 2)
TukeyHSD(anova_age_pow,conf.level=.95)
plot(TukeyHSD(anova_age_pow, conf.level=.95), las = 2)
TukeyHSD(anova_age_uni,conf.level=.95)
plot(TukeyHSD(anova_age_uni, conf.level=.95), las = 2)
TukeyHSD(anova_age_ben,conf.level=.95)
plot(TukeyHSD(anova_age_ben, conf.level=.95), las = 2)
```

## Ethnicity
 * ANOVA & TukeyHSD test: Except HEDONISM, TRADITION, and BENEVOLENCE, all values are influenced by ethnicity

```{r}
#Data cleaning
hv_eth_a <- hv_analysis %>% filter(Ethnicity_Select %in% c("White (A person having origins in any of the original peoples of Europe, the Middle East, or North Africa.)","Asian (A person having origins in any of the original peoples of the Far East, Southeast Asia, or the Indian subcontinent)","Black (A person having origins in any of the black racial groups of Africa.)","Hispanic/Latino/Spanish origin (A person of Cuban, Mexican, Puerto Rican, South or Central American, or other Spanish culture or origin, regardless of race)") )
hv_mean_eth <- hv_eth_a[,c(2,4,6,7,10,12,13:40)]
names(hv_mean_eth)[21:30] <- c("ACHIEVEMENT", "BENEVOLENCE", "CONFORMITY", "HEDONISM", "POWER", "SECURITY", "SELF_DIRECTION", "STIMULATION", "TRADITION", "UNIVERSALISM")
hv_complete_eth <- complete.cases(hv_mean_eth [, 1:30])
hv_final_eth <- hv_mean_eth[hv_complete_eth, 1:30]
hv_final_eth <- hv_final_eth %>% mutate(Ethnicity_Select_g=ifelse(Ethnicity_Select == "White (A person having origins in any of the original peoples of Europe, the Middle East, or North Africa.)","White",
                                         ifelse(Ethnicity_Select == "Asian (A person having origins in any of the original peoples of the Far East, Southeast Asia, or the Indian subcontinent)","Asian",
                                                ifelse(Ethnicity_Select == "Black (A person having origins in any of the black racial groups of Africa.)","Black", "Hispanic"
                                                ))))

#ANOVA
anova_eth_hed <- aov(HEDONISM ~ Ethnicity_Select_g, data = hv_final_eth)
summary(anova_eth_hed)
anova_eth_sel <- aov(SELF_DIRECTION ~ Ethnicity_Select_g, data = hv_final_eth)
summary(anova_eth_sel)
anova_eth_sti <- aov(STIMULATION ~ Ethnicity_Select_g, data = hv_final_eth)
summary(anova_eth_sti)
anova_eth_sec <- aov(SECURITY ~ Ethnicity_Select_g, data = hv_final_eth)
summary(anova_eth_sec)
anova_eth_con <- aov(CONFORMITY ~ Ethnicity_Select_g, data = hv_final_eth)
summary(anova_eth_con)
anova_eth_tra <- aov(TRADITION ~ Ethnicity_Select_g, data = hv_final_eth)
summary(anova_eth_tra)
anova_eth_ach <- aov(ACHIEVEMENT ~ Ethnicity_Select_g, data = hv_final_eth)
summary(anova_eth_ach)
anova_eth_pow <- aov(POWER ~ Ethnicity_Select_g, data = hv_final_eth)
summary(anova_eth_pow)
anova_eth_uni <- aov(UNIVERSALISM ~ Ethnicity_Select_g, data = hv_final_eth)
summary(anova_eth_uni)
anova_eth_ben <- aov(BENEVOLENCE ~ Ethnicity_Select_g, data = hv_final_eth)
summary(anova_eth_ben)

#TukeyHSD test
TukeyHSD(anova_eth_hed,conf.level=.95)
plot(TukeyHSD(anova_eth_hed, conf.level=.95), las = 2)
TukeyHSD(anova_eth_sel,conf.level=.95)
plot(TukeyHSD(anova_eth_sel, conf.level=.95), las = 2)
TukeyHSD(anova_eth_sti,conf.level=.95)
plot(TukeyHSD(anova_eth_sti, conf.level=.95), las = 2)
TukeyHSD(anova_eth_sec,conf.level=.95)
plot(TukeyHSD(anova_eth_sec, conf.level=.95), las = 2)
TukeyHSD(anova_eth_con,conf.level=.95)
plot(TukeyHSD(anova_eth_con, conf.level=.95), las = 2)
TukeyHSD(anova_eth_tra,conf.level=.95)
plot(TukeyHSD(anova_eth_tra, conf.level=.95), las = 2)
TukeyHSD(anova_eth_ach,conf.level=.95)
plot(TukeyHSD(anova_eth_ach, conf.level=.95), las = 2)
TukeyHSD(anova_eth_pow,conf.level=.95)
plot(TukeyHSD(anova_eth_pow, conf.level=.95), las = 2)
TukeyHSD(anova_eth_uni,conf.level=.95)
plot(TukeyHSD(anova_eth_uni, conf.level=.95), las = 2)
TukeyHSD(anova_eth_ben,conf.level=.95)
plot(TukeyHSD(anova_eth_ben, conf.level=.95), las = 2)
```

## Education level
 * ANOVA: TRADITION, STIMULATION, SELF-DIRECTION are influenced by education level.
 * TukeyHSD test: STIMULATION, SELF-DIRECTION are influenced by education level.

```{r}
#Data cleaning
hv_mean3 <- hv_edu[,c(2,4,6,7,10,12,13:40,61)]
names(hv_mean3)[25:35] <- c("ACHIEVEMENT", "BENEVOLENCE", "CONFORMITY", "HEDONISM", "POWER", "SECURITY", "SELF_DIRECTION", "STIMULATION", "TRADITION", "UNIVERSALISM", "group")
hv_complete_a3 <- complete.cases(hv_mean3[, 1:35])
hv_final_edu <- hv_mean3[hv_complete_a3, 1:35]

#ANOVA
anova_edu_hed <- aov(HEDONISM ~ group, data = hv_final_edu)
summary(anova_edu_hed)
anova_edu_sel <- aov(SELF_DIRECTION ~ group, data = hv_final_edu)
summary(anova_edu_sel)
anova_edu_sti <- aov(STIMULATION ~ group, data = hv_final_edu)
summary(anova_edu_sti)
anova_edu_sec <- aov(SECURITY ~ group, data = hv_final_edu)
summary(anova_edu_sec)
anova_edu_con <- aov(CONFORMITY ~ group, data = hv_final_edu)
summary(anova_edu_con)
anova_edu_tra <- aov(TRADITION ~ group, data = hv_final_edu)
summary(anova_edu_tra)
anova_edu_ach <- aov(ACHIEVEMENT ~ group, data = hv_final_edu)
summary(anova_edu_ach)
anova_edu_pow <- aov(POWER ~ group, data = hv_final_edu)
summary(anova_edu_pow)
anova_edu_uni <- aov(UNIVERSALISM ~ group, data = hv_final_edu)
summary(anova_edu_uni)
anova_edu_ben <- aov(BENEVOLENCE ~ group, data = hv_final_edu)
summary(anova_edu_ben)

#TukeyHSD test: Education level group means are significantly different at the 95 percent confidence level
TukeyHSD(anova_edu_hed,conf.level=.95)
plot(TukeyHSD(anova_edu_hed, conf.level=.95), las = 2)
TukeyHSD(anova_edu_sel,conf.level=.95)
plot(TukeyHSD(anova_edu_sel, conf.level=.95), las = 2)
TukeyHSD(anova_edu_sti,conf.level=.95)
plot(TukeyHSD(anova_edu_sti, conf.level=.95), las = 2)
TukeyHSD(anova_edu_sec,conf.level=.95)
plot(TukeyHSD(anova_edu_sec, conf.level=.95), las = 2)
TukeyHSD(anova_edu_con,conf.level=.95)
plot(TukeyHSD(anova_edu_con, conf.level=.95), las = 2)
TukeyHSD(anova_edu_tra,conf.level=.95)
plot(TukeyHSD(anova_edu_tra, conf.level=.95), las = 2)
TukeyHSD(anova_edu_ach,conf.level=.95)
plot(TukeyHSD(anova_edu_ach, conf.level=.95), las = 2)
TukeyHSD(anova_edu_pow,conf.level=.95)
plot(TukeyHSD(anova_edu_pow, conf.level=.95), las = 2)
TukeyHSD(anova_edu_uni,conf.level=.95)
plot(TukeyHSD(anova_edu_uni, conf.level=.95), las = 2)
TukeyHSD(anova_edu_ben,conf.level=.95)
plot(TukeyHSD(anova_edu_ben, conf.level=.95), las = 2)
```

## Income level
 * ANOVA: SECURITY, STIMULATION, SELF-DIRECTION are influenced by education level.
 * TukeyHSD test: STIMULATION, SELF-DIRECTION are influenced by education level.

```{r}
#Data cleaning
hv_mean4 <- hv_income[,c(2,4,6,7,10,12,13:40,61)]
names(hv_mean4)[25:35] <- c("ACHIEVEMENT", "BENEVOLENCE", "CONFORMITY", "HEDONISM", "POWER", "SECURITY", "SELF_DIRECTION", "STIMULATION", "TRADITION", "UNIVERSALISM", "group")
hv_complete_a4 <- complete.cases(hv_mean4[, 1:35])
hv_final_inc<- hv_mean4[hv_complete_a4, 1:35]

#ANOVA
anova_inc_hed <- aov(HEDONISM ~ group, data = hv_final_inc)
summary(anova_inc_hed)
anova_inc_sel <- aov(SELF_DIRECTION ~ group, data = hv_final_inc)
summary(anova_inc_sel)
anova_inc_sti <- aov(STIMULATION ~ group, data = hv_final_inc)
summary(anova_inc_sti)
anova_inc_sec <- aov(SECURITY ~ group, data = hv_final_inc)
summary(anova_inc_sec)
anova_inc_con <- aov(CONFORMITY ~ group, data = hv_final_inc)
summary(anova_inc_con)
anova_inc_tra <- aov(TRADITION ~ group, data = hv_final_inc)
summary(anova_inc_tra)
anova_inc_ach <- aov(ACHIEVEMENT ~ group, data = hv_final_inc)
summary(anova_inc_ach)
anova_inc_pow <- aov(POWER ~ group, data = hv_final_inc)
summary(anova_inc_pow)
anova_inc_uni <- aov(UNIVERSALISM ~ group, data = hv_final_inc)
summary(anova_inc_uni)
anova_inc_ben <- aov(BENEVOLENCE ~ group, data = hv_final_inc)
summary(anova_inc_ben)

#TukeyHSD test
TukeyHSD(anova_inc_hed,conf.level=.95)
plot(TukeyHSD(anova_inc_hed, conf.level=.95), las = 2)
TukeyHSD(anova_inc_sel,conf.level=.95)
plot(TukeyHSD(anova_inc_sel, conf.level=.95), las = 2)
TukeyHSD(anova_inc_sti,conf.level=.95)
plot(TukeyHSD(anova_inc_sti, conf.level=.95), las = 2)
TukeyHSD(anova_inc_sec,conf.level=.95)
plot(TukeyHSD(anova_inc_sec, conf.level=.95), las = 2)
TukeyHSD(anova_inc_con,conf.level=.95)
plot(TukeyHSD(anova_inc_con, conf.level=.95), las = 2)
TukeyHSD(anova_inc_tra,conf.level=.95)
plot(TukeyHSD(anova_inc_tra, conf.level=.95), las = 2)
TukeyHSD(anova_inc_ach,conf.level=.95)
plot(TukeyHSD(anova_inc_ach, conf.level=.95), las = 2)
TukeyHSD(anova_inc_pow,conf.level=.95)
plot(TukeyHSD(anova_inc_pow, conf.level=.95), las = 2)
TukeyHSD(anova_inc_uni,conf.level=.95)
plot(TukeyHSD(anova_inc_uni, conf.level=.95), las = 2)
TukeyHSD(anova_inc_ben,conf.level=.95)
plot(TukeyHSD(anova_inc_ben, conf.level=.95), las = 2)
```

# ANOVA & Bonferroni correction
 * Bonferroni correction: a post hoc method to counteract the multiple comparisons problem like Tukey test. P-value less than the threshold (0.05/total number of comparisons or tests being performed) means the difference between the pairs is statistically significant.
 
## Age
 * ANOVA & Bonferroni: All values are influenced by age
 
```{r}
bon_age_hed <-LSD.test(anova_age_hed,"group",p.adj="bonferroni",group=F)
bon_age_hed
bon_age_sel <-LSD.test(anova_age_sel,"group",p.adj="bonferroni",group=F)
bon_age_sel

bon_age_sti <-LSD.test(anova_age_sti,"group",p.adj="bonferroni",group=F)
bon_age_sti

bon_age_sec <-LSD.test(anova_age_sec,"group",p.adj="bonferroni",group=F)
bon_age_sec

bon_age_con <-LSD.test(anova_age_con,"group",p.adj="bonferroni",group=F)
bon_age_con

bon_age_tra <-LSD.test(anova_age_tra,"group",p.adj="bonferroni",group=F)
bon_age_tra

bon_age_ach <-LSD.test(anova_age_ach,"group",p.adj="bonferroni",group=F)
bon_age_ach

bon_age_pow <-LSD.test(anova_age_pow,"group",p.adj="bonferroni",group=F)
bon_age_pow

bon_age_uni <-LSD.test(anova_age_uni,"group",p.adj="bonferroni",group=F)
bon_age_uni

bon_age_ben <-LSD.test(anova_age_ben,"group",p.adj="bonferroni",group=F)
bon_age_ben
```

## Ethnicity
 * ANOVA & Bonferroni: Except HEDONISM, TRADITION, and BENEVOLENCE, all values are influenced by ethnicity
 
```{r}
bon_eth_hed <-LSD.test(anova_eth_hed,"Ethnicity_Select_g",p.adj="bonferroni",group=F)
bon_eth_hed

bon_eth_sel <-LSD.test(anova_eth_sel,"Ethnicity_Select_g",p.adj="bonferroni",group=F)
bon_eth_sel

bon_eth_sti <-LSD.test(anova_eth_sti,"Ethnicity_Select_g",p.adj="bonferroni",group=F)
bon_eth_sti

bon_eth_sec <-LSD.test(anova_eth_sec,"Ethnicity_Select_g",p.adj="bonferroni",group=F)
bon_eth_sec

bon_eth_con <-LSD.test(anova_eth_con,"Ethnicity_Select_g",p.adj="bonferroni",group=F)
bon_eth_con

bon_eth_tra <-LSD.test(anova_eth_tra,"Ethnicity_Select_g",p.adj="bonferroni",group=F)
bon_eth_tra

bon_eth_ach <-LSD.test(anova_eth_ach,"Ethnicity_Select_g",p.adj="bonferroni",group=F)
bon_eth_ach

bon_eth_pow <-LSD.test(anova_eth_pow,"Ethnicity_Select_g",p.adj="bonferroni",group=F)
bon_eth_pow

bon_eth_uni <-LSD.test(anova_eth_uni,"Ethnicity_Select_g",p.adj="bonferroni",group=F)
bon_eth_uni

bon_eth_ben <-LSD.test(anova_eth_ben,"Ethnicity_Select_g",p.adj="bonferroni",group=F)
bon_eth_ben
```

## Education level
 * ANOVA: TRADITION, STIMULATION, SELF-DIRECTION are influenced by education level.
 * Bonferroni: STIMULATION is influenced by education level.
 
```{r}
bon_edu_hed <-LSD.test(anova_edu_hed,"group",p.adj="bonferroni",group=F)
bon_edu_hed

bon_edu_sel <-LSD.test(anova_edu_sel,"group",p.adj="bonferroni",group=F)
bon_edu_sel

bon_edu_sti <-LSD.test(anova_edu_sti,"group",p.adj="bonferroni",group=F)
bon_edu_sti

bon_edu_sec <-LSD.test(anova_edu_sec,"group",p.adj="bonferroni",group=F)
bon_edu_sec

bon_edu_con <-LSD.test(anova_edu_con,"group",p.adj="bonferroni",group=F)
bon_edu_con

bon_edu_tra <-LSD.test(anova_edu_tra,"group",p.adj="bonferroni",group=F)
bon_edu_tra

bon_edu_ach <-LSD.test(anova_edu_ach,"group",p.adj="bonferroni",group=F)
bon_edu_ach

bon_edu_pow <-LSD.test(anova_edu_pow,"group",p.adj="bonferroni",group=F)
bon_edu_pow

bon_edu_uni <-LSD.test(anova_edu_uni,"group",p.adj="bonferroni",group=F)
bon_edu_uni

bon_edu_ben <-LSD.test(anova_edu_ben,"group",p.adj="bonferroni",group=F)
bon_edu_ben
```

## Income level
 * ANOVA: SECURITY, STIMULATION, SELF-DIRECTION are influenced by education level.
 * Bonferroni: STIMULATION, SELF-DIRECTION are influenced by education level.
 
```{r}
bon_inc_hed <-LSD.test(anova_inc_hed,"group",p.adj="bonferroni",group=F)
bon_inc_hed

bon_inc_sel <-LSD.test(anova_inc_sel,"group",p.adj="bonferroni",group=F)
bon_inc_sel

bon_inc_sti <-LSD.test(anova_inc_sti,"group",p.adj="bonferroni",group=F)
bon_inc_sti

bon_inc_sec <-LSD.test(anova_inc_sec,"group",p.adj="bonferroni",group=F)
bon_inc_sec

bon_inc_con <-LSD.test(anova_inc_con,"group",p.adj="bonferroni",group=F)
bon_inc_con

bon_inc_tra <-LSD.test(anova_inc_tra,"group",p.adj="bonferroni",group=F)
bon_inc_tra

bon_inc_ach <-LSD.test(anova_inc_ach,"group",p.adj="bonferroni",group=F)
bon_inc_ach

bon_inc_pow <-LSD.test(anova_inc_pow,"group",p.adj="bonferroni",group=F)
bon_inc_pow

bon_inc_uni <-LSD.test(anova_inc_uni,"group",p.adj="bonferroni",group=F)
bon_inc_uni

bon_inc_ben <-LSD.test(anova_inc_ben,"group",p.adj="bonferroni",group=F)
bon_inc_ben
```
 
# ANOVA & TukeyHSD test & Bonferroni correction results
 * There are conflicts between the results of AVOVA and TukeyHSD test in education level and income level
   + Education level: ANOVA shows TRADITION, STIMULATION, SELF-DIRECTION are influenced by education level, but TukeyHSD says only STIMULATION, SELF-DIRECTION are influenced by education level
   + Income level: ANOVA shows SECURITY, STIMULATION, SELF-DIRECTION are influenced by education level, but TukeyHSD says only STIMULATION, SELF-DIRECTION are influenced by education level
 * There is a conflict between the results of TukeyHSD test and Bonferroni correction in education level
   + Education level: TukeyHSD shows STIMULATION, SELF-DIRECTION are influenced by education level, but Bonferroni says only STIMULATION is influenced by education level.
  
## TukeyHSD test results
 * All values are influenced by Age 
   + Age seems to be the most influential demographic factor which affects individual's value prioritization in a citizen science setting). 
 * STIMULATION, SELF-DIRECTION are influenced by age, ethnicity, education level, and income level
   + Regardless of demographic features, citizen scientists seem to share STIMULATION (excitement, novelty, challenge) and SELF-DIRECTION (independent thought and action--choosing, creating, exploring) as their common values and those values are salient motivation of citizen scientists who participate in the Zooniverse projects.   
 * Except HEDONISM, TRADITION, and BENEVOLENCE, all values are influenced by ethnicity
   + Ethnicity seems to be less influential compared to age, but impact values.  
 
## Bonferroni correction results
 * All values are influenced by Age
   + Age seems to be the most influential demographic factor which affects individual's value prioritization in a citizen science setting). 
 * STIMULATION is influenced by age, ethnicity, education level, and income level
   + Regardless of demographic features, citizen scientists seem to share STIMULATION (excitement, novelty, challenge)  as their common value and this value is a salient motivation of citizen scientists who participate in the Zooniverse projects.   
 * Except HEDONISM, TRADITION, and BENEVOLENCE, all values are influenced by ethnicity
   + Ethnicity seems to be less influential compared to age, but impact values.  


