---
title: "study2_analysis"
author: "Ellie Jeong"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(stringr)
library(tidyverse)
library(gtsummary)
library(data.table)
library(knitr)
library(kableExtra)
library(DT)
library(gt)
library(webshot2)
library(dunn.test)
library(purrr)

# Creating a dataset: "merged_male_female.csv"
# setwd("/Users/hp/Dissertation_value_demo_data/study2")
# pvq <- read.csv("pvq.users.data.csv") #N = 5436 (Study1 stats. Female: 3,141, Male: 2,020, Other:192)
# demo <- read.csv("complete_responses_noipdupes.csv") #N= 5879
# 
# demo <- demo %>%
#   mutate(
#     gender_g = str_trim(Gender_Select),
#     gender_g = recode(
#       gender_g,
#       "Female (including transgender women)" = "female",
#       "Male (including transgender men)" = "male"
#     ),
#     gender_g = case_when(
#       gender_g %in% c("female", "male") ~ gender_g,
#       TRUE ~ "other"
#     )
#   )
# 
# # Merge two datasets: N = 5436/ Female = 3,033 (valid email = 1,817), Male = 1963, Other = 271, NA = 169
# all <- pvq %>% left_join(demo, by= "ResponseId")

# Save a dataset
#write.csv(all, "merged_male_female.csv", row.names = TRUE)


# Import data
setwd("/Volumes/cbjackson2/values_ellie/study2/data")

demo_value <- read.csv("merged_male_female.csv", header = TRUE, fileEncoding = "latin1")[, -1]
survey <- read.csv("final_zooniverse_survey.csv", header = TRUE, fileEncoding = "latin1")
workshop <- read_csv("workshop_participant.csv")
```

## Data cleaning

```{r, include=FALSE}
# Clean data
## Demo_value
demo_value <- demo_value %>% mutate(email = str_trim(RaffleEmail))
demo_value$email <- tolower(str_trim(demo_value$email))

## Survey
survey <- survey[-c(1,2),]

#which(names(survey) == "Q26_1")
#survey <- survey %>% rename(email = Q26_1)

survey <- survey %>%
  mutate(email = str_trim(Q26_1))

survey$email <- tolower(str_trim(survey$email))

# Check emails in survey but NOT in demo_value
# "gg2032@tc.columbia.edu" "katie.burnette@ucr.edu" "" 

setdiff(survey$email, demo_value$email)

# Recode emails in 2021 (demo_value) data to match 2026 (survey) data
#gg2032@tc.columbia.edu (survey) = gxgund@gmail.com (demo_value)
#katie.burnette@ucr.edu (survey) = katiec@ucr.edu (demo_value)

demo_value$email <- dplyr::recode(demo_value$email, 
                                                   `gxgund@gmail.com` = "gg2032@tc.columbia.edu", 
                                                   `katiec@ucr.edu` = "katie.burnette@ucr.edu")

# Merge data
merged <- survey %>% left_join(demo_value, by = "email")

# Select rows
data <- merged %>% filter(email !="")

# Check meta-data
metadata <- data[,c(4,14,15,59,61,110,114,119,120)] 

which(duplicated(data$email)) #row 5, 51 -> choose the first response
data <- data[c(-5,-51),]
sum(is.na(data$ResponseId.y)) #N = 0 (submitted email addresses different from the previous ones)


# Create a dataset for analysis
analysis <- data[,c(9,21:59,62:71,82:91,94:97,125,126,128,131,135,276)]

# Fix erroneous comma in Activity column
analysis$Q61 <- str_replace_all(analysis$Q61, fixed("responses, announcements"), "responses/ announcements")

# Recode Likert scale
analysis <- analysis %>%
  mutate(across(
    c(Q78_1, Q78_2, Q78_3),
    ~ ifelse(. == "7", "I do not know", .)
  ))

# Recode age, ethnicity, education, income level

### ETH 
single_eth <- c("White (A person having origins in any of the original peoples of Europe, the Middle East, or North Africa.)","Asian (A person having origins in any of the original peoples of the Far East, Southeast Asia, or the Indian subcontinent)","Black (A person having origins in any of the black racial groups of Africa.)","Hispanic/Latino/Spanish origin (A person of Cuban, Mexican, Puerto Rican, South or Central American, or other Spanish culture or origin, regardless of race)","Another race - Please specify","Prefer not to answer")

analysis$single_eth <- 
  ifelse(!analysis$Ethnicity_Select %in% single_eth,"Multi-racial",
         paste0(analysis$Ethnicity_Select))


analysis$single_eth <- dplyr::recode(analysis$single_eth, `White (A person having origins in any of the original peoples of Europe, the Middle East, or North Africa.)` = "White",`Asian (A person having origins in any of the original peoples of the Far East, Southeast Asia, or the Indian subcontinent)` =  "Asian", `Black (A person having origins in any of the black racial groups of Africa.)`= "Black", `Hispanic/Latino/Spanish origin (A person of Cuban, Mexican, Puerto Rican, South or Central American, or other Spanish culture or origin, regardless of race)` ="Hispanic", `Another race - Please specify` = "Other", `Prefer not to answer`="No Response")


analysis$single_eth <- factor(analysis$single_eth, levels=c('Asian', 'Black', 'Hispanic', 'Multi-racial','White', 'Other',"No Response"))

### AGE 
analysis <- analysis %>% 
  mutate(AgeGroup = case_when(
    Age > 64 ~ 'Above 64',                                           
    Age >= 55  & Age <= 64 ~ '55-64',
    Age >= 45  & Age <= 54 ~ '45-54',
    Age >= 35  & Age <= 44 ~ '35-44',
    Age >= 25  & Age <= 34 ~ '25-34',
    Age >= 18  & Age <= 24 ~ '18-24')) 

# Schooling
analysis$Education <- dplyr::recode(analysis$SchoolHighestEdu, 
                                                   `Short-cycle tertiary education, e.g. vocational program` = "Vocational", 
                                                   `Post-secondary non-tertiary education` = "Vocational",
                                                   `Lower secondary education` = "< Bachelors",
                                                   `Primary education` = "< Bachelors",
                                                   `Upper secondary education` = "< Bachelors",
                                                   `Early childhood Education` = "< Bachelors",
                                                   `Bachelor's or equivalent` = "Bachelor's",
                                                   `Master's or equivalent` = "Master's",
                                                   `Doctoral or equivalent` = "Doctorate",
                                                   `Prefer not to answer` = "No Response"
)

analysis$Education <- factor(analysis$Education, levels=c('< Bachelors', 'Bachelor\'s','Vocational',
                                                                                        'Master\'s','Doctorate','No Response'))


analysis <- analysis %>% 
  mutate(Income=ifelse(Income %in% c("Less than $1,000","$1,000 to $1,999","$2,000 to $2,999"), "Low",
                       ifelse(Income %in% c("$3,000 to $3,999","$4,000 to $4,999"),"Middle",
                              ifelse(Income %in% c("$5,000 or more"),"High", NA))))

analysis$Income <- factor(analysis$Income, levels=c('Low','Middle','High'))

# Recode Q23 → self_conflict and Q79 → power_conflict
value_label_map <- c(
  "Doing what is expected/avoiding upsetting others/following shared rules and norms"    = "Conformity",
  "Keeping things safe/stable/protected from risks or threats"                           = "Security",
  "Respecting long-standing ways of doing things and established customs"                = "Tradition",
  "Being helpful/dependable/looking after people you feel close to in the community"     = "Benevolence",
  "Fairness and equal treatment for everyone/concern for people and nature beyond your immediate circle" = "Universalism",
  "Demonstrating skill and excellence/achieving high standards/being seen as competent"  = "Achievement",
  "Enjoying activities that feel pleasant/fun/comfortable"                               = "Hedonism",
  "Seeking novelty/excitement/new challenges"                                            = "Stimulation",
  "Having a meaningful say in how things are done"                                       = "Power",
  "Having room to decide for themselves"                                                 = "Self-direction"
)

analysis <- analysis %>%
  mutate(
    self_conflict_1  = dplyr::recode(str_trim(str_split_fixed(Q23, ",", 2)[, 1]), !!!value_label_map),
    self_conflict_2  = dplyr::recode(str_trim(str_split_fixed(Q23, ",", 2)[, 2]), !!!value_label_map),
    power_conflict_1 = dplyr::recode(str_trim(str_split_fixed(Q79, ",", 2)[, 1]), !!!value_label_map),
    power_conflict_2 = dplyr::recode(str_trim(str_split_fixed(Q79, ",", 2)[, 2]), !!!value_label_map)
  )
```

## Data summary

### Income

-   Low: less than \$3,000

-   Mid: \$3,000 - \$ 4,999

-   High: \$5,000 or more

```{r pressure, echo=FALSE}
## Age
age_t <- analysis %>% 
  dplyr::filter(AgeGroup != "NA") %>%
  dplyr::group_by(AgeGroup) %>% 
  dplyr::summarize(Frequency = n()) %>%
  dplyr::arrange(desc(Frequency)) %>%
  dplyr::mutate(Percent = round(Frequency / sum(Frequency), digits = 2) * 100)

names(age_t)[1] <- "Age"

## Race
race_t <- analysis %>% 
  dplyr::filter(single_eth != "NA") %>%
  dplyr::group_by(single_eth) %>% 
  dplyr::summarize(Frequency = n()) %>%
  dplyr::arrange(desc(Frequency)) %>%
  dplyr::mutate(Percent = round(Frequency / sum(Frequency), digits = 2) * 100)

names(race_t)[1] <- "Race"

## Education
edu_t <- analysis %>% 
  dplyr::filter(Education != "NA") %>%
  dplyr::group_by(Education) %>% 
  dplyr::summarize(Frequency = n()) %>%
  dplyr::arrange(desc(Frequency)) %>%
  dplyr::mutate(Percent = round(Frequency / sum(Frequency), digits = 2) * 100)

names(edu_t)[1] <- "Education"

## Income
income_t <- analysis %>% 
  dplyr::filter(Income != "NA") %>%
  dplyr::group_by(Income) %>% 
  dplyr::summarize(Frequency = n()) %>%
  dplyr::arrange(desc(Frequency)) %>%
  dplyr::mutate(Percent = round(Frequency / sum(Frequency), digits = 2) * 100)

names(income_t)[1] <- "Income"

datatable(age_t)
age_t %>% gt() %>% gtsave("age_t.png")

datatable(race_t)
race_t %>% gt() %>% gtsave("race_t.png")

datatable(edu_t)
edu_t %>% gt() %>% gtsave("edu_t.png")

datatable(income_t)
income_t %>% gt() %>% gtsave("income_t.png")
```

## Citizen Science Experience: Descriptive Statistics

```{r experience_stats, echo=FALSE}

# Rename columns
analysis <- analysis %>%
  rename(
    Experience = Q34,
    Frequency  = Q37,
    Projects   = Q60,
    Activity   = Q61
  )

# Experience
exp_t <- analysis %>%
  filter(!is.na(Experience) & Experience != "") %>%
  group_by(Experience) %>%
  summarize(Frequency = n()) %>%
  arrange(desc(Frequency)) %>%
  mutate(Percent = round(Frequency / sum(Frequency), digits = 2) * 100)

# Frequency
freq_t <- analysis %>%
  filter(!is.na(Frequency) & Frequency != "") %>%
  group_by(Frequency) %>%
  summarize(Count = n()) %>%
  arrange(desc(Count)) %>%
  mutate(Percent = round(Count / sum(Count), digits = 2) * 100)

# Projects
proj_t <- analysis %>%
  filter(!is.na(Projects) & Projects != "") %>%
  group_by(Projects) %>%
  summarize(Frequency = n()) %>%
  arrange(desc(Frequency)) %>%
  mutate(Percent = round(Frequency / sum(Frequency), digits = 2) * 100)

# Activity (split comma-separated values)
act_t <- analysis %>%
  filter(!is.na(Activity) & Activity != "") %>%
  select(Activity) %>%
  separate_rows(Activity, sep = ",") %>%
  mutate(Activity = str_trim(Activity)) %>%
  group_by(Activity) %>%
  summarize(Frequency = n()) %>%
  arrange(desc(Frequency)) %>%
  mutate(Percent = round(Frequency / 50, digits = 2) * 100)

datatable(exp_t)
exp_t %>% gt() %>% gtsave("exp_t.png")

datatable(freq_t)
freq_t %>% gt() %>% gtsave("freq_t.png")

datatable(proj_t)
proj_t %>% gt() %>% gtsave("proj_t.png")

datatable(act_t)
act_t %>% gt() %>% gtsave("act_t.png")
```

## Contribution-Value score

### Kruskal-Wallis tests: each of the 10 value scores & Experience, Frequency, and Projects, and Activity (non-parametric test that compares average ranks of ordinal/continuous values of the outcome variable across groups/ ANOVA compares means when data is normally distributed)

-   Security score is significantly associated with the frequency of contribution (χ² = 16.02, p = .014). However, post-hoc Dunn tests with multiple-comparison correction did not identify significant differences between any specific frequency groups.

### Spearman correlations: value scores & each Activity type

-   Power is positively associated with reading instructions or reference materials (ρ = .314, p = .026)
-   Universalism is positively associated with reporting bugs or suggesting features (ρ = .299, p = .035)
-   After multiple-comparison correction (Benjamini–Hochberg correction), they are no longer significant.  

```{r contribution_relationship, echo=FALSE}
# Prepare dataset: value scores + contribution variables
value_score_cols <- colnames(analysis)[41:50]
value_labels     <- str_remove_all(value_score_cols, regex("score", ignore_case = TRUE))

contrib_data <- analysis %>%
  select(all_of(value_score_cols), Experience, Frequency, Projects, Activity) %>%
  mutate(across(all_of(value_score_cols), as.numeric))

colnames(contrib_data)[1:10] <- value_labels

# Kruskal-Wallis: each value score vs Experience, Frequency, Projects
kw_results <- map_dfr(c("Experience", "Frequency", "Projects"), function(contrib) {
  map_dfr(value_labels, function(val) {
    test <- tryCatch(
      kruskal.test(contrib_data[[val]] ~ contrib_data[[contrib]]),
      error = function(e) list(statistic = NA, parameter = NA, p.value = NA)
    )
    data.frame(
      Value        = val,
      Contribution = contrib,
      Chi_sq       = round(test$statistic, 3),
      df           = test$parameter,
      p_value      = round(test$p.value, 3)
    )
  })
}) %>%
  mutate(Sig = case_when(
    p_value < 0.001 ~ "***",
    p_value < 0.01  ~ "**",
    p_value < 0.05  ~ "*",
    p_value < 0.1   ~ ".",
    TRUE            ~ ""
  ))

# Use p < 0.1 threshold for exploratory analysis
kw_sig <- kw_results %>% filter(p_value < 0.1)
datatable(kw_sig)
kw_sig %>% gt() %>% gtsave("kw_results.png")

# Post-hoc Dunn test for each marginally significant KW pair (Holm correction)
cat("Marginally significant KW pairs (p < 0.1):", nrow(kw_sig), "\n")

dunn_results <- map_dfr(seq_len(nrow(kw_sig)), function(i) {
  val     <- kw_sig$Value[i]
  contrib <- kw_sig$Contribution[i]

  dt <- dunn.test(contrib_data[[val]], contrib_data[[contrib]],
                  method = "holm", altp = TRUE)

  data.frame(
    Value        = val,
    Contribution = contrib,
    Comparison   = dt$comparisons,
    Z            = round(dt$Z, 3),
    p_adj        = round(dt$altP.adjusted, 3),
    Sig          = case_when(
      dt$altP.adjusted < 0.001 ~ "***",
      dt$altP.adjusted < 0.01  ~ "**",
      dt$altP.adjusted < 0.05  ~ "*",
      dt$altP.adjusted < 0.1   ~ ".",
      TRUE                     ~ ""
    )
  )
})

datatable(dunn_results)

dunn_sig <- dunn_results %>% filter(p_adj < 0.1)
if (nrow(dunn_sig) > 0) {
  dunn_sig %>% gt() %>% gtsave("dunn_results.png")
} else {
  cat("No pairwise comparisons reached p < 0.1 after Holm correction.\n")
}

# Boxplots for all marginally significant KW pairs
if (nrow(kw_sig) > 0) {
  walk(seq_len(nrow(kw_sig)), function(i) {
    val     <- kw_sig$Value[i]
    contrib <- kw_sig$Contribution[i]
    p_val   <- kw_sig$p_value[i]

    plot_data <- contrib_data %>%
      select(all_of(val), all_of(contrib)) %>%
      filter(!is.na(.data[[contrib]]), .data[[contrib]] != "")

    p <- ggplot(plot_data, aes(x = .data[[contrib]], y = .data[[val]])) +
      geom_boxplot(fill = "#a8c8e8", color = "#1a5fa8", outlier.shape = 16) +
      geom_jitter(width = 0.15, alpha = 0.5, color = "#1a5fa8") +
      labs(
        title    = paste(val, "by", contrib),
        subtitle = paste0("Kruskal-Wallis p = ", p_val),
        x        = contrib,
        y        = paste(val, "Score")
      ) +
      theme_minimal() +
      theme(axis.text.x = element_text(angle = 30, hjust = 1))

    print(p)
    ggsave(paste0("boxplot_", val, "_", contrib, ".png"),
           plot = p, width = 7, height = 5, dpi = 300)
  })
}

# Heatmap of p-values
kw_results %>%
  ggplot(aes(x = Contribution, y = Value, fill = p_value)) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste0(Chi_sq, Sig)), size = 3.5) +
  scale_fill_gradient(low = "#1a5fa8", high = "#f0f0f0", name = "p-value",
                      limits = c(0, 0.05), oob = scales::squish) +
  labs(
    title    = "Kruskal-Wallis: Value Scores vs Contribution Patterns",
    subtitle = "Cell = chi-squared statistic; * p<.05  ** p<.01  *** p<.001",
    x = NULL, y = NULL
  ) +
  theme_minimal()

ggsave("kw_heatmap.png", width = 8, height = 6, dpi = 300)

# Activity: split multi-select into binary dummy variables, then Spearman correlate with value scores
activity_dummies <- contrib_data %>%
  select(all_of(value_labels), Activity) %>%
  separate_rows(Activity, sep = ",") %>%
  mutate(Activity = str_trim(Activity)) %>%
  filter(Activity != "") %>%
  mutate(present = 1) %>%
  pivot_wider(names_from = Activity, values_from = present,
              values_fill = 0, values_fn = max)

activity_cols <- setdiff(colnames(activity_dummies), value_labels)

activity_cor <- map_dfr(activity_cols, function(act) {
  map_dfr(value_labels, function(val) {
    test <- tryCatch(
      cor.test(activity_dummies[[val]], activity_dummies[[act]],
               method = "spearman", exact = FALSE),
      error = function(e) list(estimate = NA, p.value = NA)
    )
    data.frame(
      Value    = val,
      Activity = act,
      rho      = round(test$estimate, 3),
      p_value  = round(test$p.value, 3)
    )
  })
}) %>%
  mutate(Sig = case_when(
    p_value < 0.001 ~ "***",
    p_value < 0.01  ~ "**",
    p_value < 0.05  ~ "*",
    p_value < 0.1   ~ ".",
    TRUE            ~ ""
  ))

activity_cor_sig <- activity_cor %>% filter(p_value < 0.05)
datatable(activity_cor_sig)
activity_cor_sig %>% gt() %>% gtsave("activity_cor.png")

activity_cor <- activity_cor %>%
  mutate(
    p_adj = p.adjust(p_value, method = "BH"),
    Sig_adj = case_when(
      p_adj < 0.001 ~ "***",
      p_adj < 0.01  ~ "**",
      p_adj < 0.05  ~ "*",
      p_adj < 0.1   ~ ".",
      TRUE          ~ ""
    )
  )

activity_cor %>% filter(p_adj < 0.05)
```

## Value Scores: means and rank

### Study 1 value analysis of the entire participants (N = 5,436)

```{r value_scores, echo=FALSE}
# Extract value score columns
value_cols_1 <- demo_value[, c((3:12),217)]

# Select females
value_cols_2 <- value_cols_1 %>%
  filter(gender_g == "female")

# Delete gender group
value_cols_1 <- value_cols_1[,-11]

# Remove "score" from column names
colnames(value_cols_1) <- str_remove_all(colnames(value_cols_1), regex("score", ignore_case = TRUE))

# Convert to numeric (in case imported as character)
value_cols_1 <- value_cols_1 %>% mutate(across(everything(), as.numeric))

# Calculate column means and rank
value_summary_1 <- data.frame(
  Value = colnames(value_cols_1),
  Mean  = colMeans(value_cols_1, na.rm = TRUE)
) %>%
  arrange(desc(Mean)) %>%
  mutate(
    Rank = row_number(),
    Mean = round(Mean, 2)
  )

# Table
datatable(value_summary_1)
value_summary_1 %>% gt() %>% gtsave("all_value_ranking.png")
```

### Study 1 female value analysis (N = 3,033)

```{r value_scores, echo=FALSE}
# Delete gender group
value_cols_2 <- value_cols_2[,-11]

# Calculate column means and rank
colnames(value_cols_2) <- str_remove_all(colnames(value_cols_2), regex("score", ignore_case = TRUE))

# Convert to numeric (in case imported as character)
value_cols_2 <- value_cols_2 %>% mutate(across(everything(), as.numeric))

value_summary_2 <- data.frame(
  Value = colnames(value_cols_2),
  Mean  = colMeans(value_cols_2, na.rm = TRUE)
) %>%
  arrange(desc(Mean)) %>%
  mutate(
    Rank = row_number(),
    Mean = round(Mean, 2)
  )

# Table
datatable(value_summary_2)
value_summary_2 %>% gt() %>% gtsave("female_study1_value_ranking.png")
```

### Study 2 female value analysis (N = 50)

```{r value_scores, echo=FALSE}

# Extract value score columns (cols 41-50 in analysis)
value_cols <- analysis[, 41:50]

# Remove "score" from column names
colnames(value_cols) <- str_remove_all(colnames(value_cols), regex("score", ignore_case = TRUE))

# Convert to numeric (in case imported as character)
value_cols <- value_cols %>% mutate(across(everything(), as.numeric))

# Calculate column means and rank
value_summary <- data.frame(
  Value = colnames(value_cols),
  Mean  = colMeans(value_cols, na.rm = TRUE)
) %>%
  arrange(desc(Mean)) %>%
  mutate(
    Rank = row_number(),
    Mean = round(Mean, 2)
  )

# Table
datatable(value_summary)
value_summary %>% gt() %>% gtsave("female_study2_value_ranking.png")

# Bar plot
ggplot(value_summary, aes(x = reorder(Value, -Mean), y = Mean, fill = Mean)) +
  geom_bar(stat = "identity", width = 0.7) +
  geom_text(aes(label = Mean), vjust = -0.4, size = 3.5) +
  scale_fill_gradient(low = "#a8c8e8", high = "#1a5fa8") +
  labs(
    title = "Average Value Scores",
    x     = "Value",
    y     = "Mean Score"
  ) +
  theme_minimal() +
  theme(
    axis.text.x  = element_text(angle = 45, hjust = 1),
    legend.position = "none"
  )

# Lollipop chart
ggplot(value_summary, aes(x = reorder(Value, Mean), y = Mean)) +
  geom_segment(aes(xend = reorder(Value, Mean), yend = 0), color = "gray70", linewidth = 0.8) +
  geom_point(aes(color = Mean), size = 5) +
  geom_text(aes(label = Mean), hjust = -0.5, size = 3.5) +
  scale_color_gradient(low = "#a8c8e8", high = "#1a5fa8") +
  coord_flip() +
  labs(
    title = "Average Value Scores",
    x     = "Value",
    y     = "Mean Score"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

ggsave("value_lollipop.png", width = 8.5, height = 6, dpi = 300)
```

### Standardized Mean Difference: Study 1 vs Study 2 women participants

```{r smd, echo=FALSE}

# Align column names
value_cols_2_num <- value_cols_2 %>% mutate(across(everything(), as.numeric))
value_cols_num   <- value_cols   %>% mutate(across(everything(), as.numeric))

n1 <- nrow(value_cols_2_num)
n2 <- nrow(value_cols_num)

smd_results <- map_dfr(colnames(value_cols_2_num), function(val) {
  x1 <- value_cols_2_num[[val]]
  x2 <- value_cols_num[[val]]

  m1 <- mean(x1, na.rm = TRUE)
  m2 <- mean(x2, na.rm = TRUE)
  s1 <- sd(x1, na.rm = TRUE)
  s2 <- sd(x2, na.rm = TRUE)

  pooled_sd <- sqrt(((n1 - 1) * s1^2 + (n2 - 1) * s2^2) / (n1 + n2 - 2))
  smd       <- (m1 - m2) / pooled_sd

  data.frame(
    Value    = val,
    Mean_S1  = round(m1, 2),
    Mean_S2  = round(m2, 2),
    SD_S1    = round(s1, 2),
    SD_S2    = round(s2, 2),
    SMD      = round(smd, 3),
    Magnitude = case_when(
      abs(smd) >= 0.8 ~ "Large",
      abs(smd) >= 0.5 ~ "Medium",
      abs(smd) >= 0.2 ~ "Small",
      TRUE            ~ "Negligible"
    )
  )
})

datatable(smd_results)
smd_results %>% gt() %>% gtsave("smd_results.png")

# Lollipop chart of SMD
ggplot(smd_results, aes(x = reorder(Value, SMD), y = SMD, color = SMD > 0)) +
  geom_segment(aes(xend = reorder(Value, SMD), yend = 0), color = "gray70", linewidth = 0.8) +
  geom_point(size = 5) +
  geom_hline(yintercept = c(-0.8, -0.5, -0.2, 0.2, 0.5, 0.8),
             linetype = "dashed", color = "gray50", linewidth = 0.4) +
  geom_hline(yintercept = 0, color = "black", linewidth = 0.6) +
  geom_text(aes(label = SMD), hjust = -0.4, size = 3.5) +
  scale_color_manual(values = c("TRUE" = "#1a5fa8", "FALSE" = "#e05a5a"),
                     labels = c("TRUE" = "S1 > S2", "FALSE" = "S2 > S1")) +
  coord_flip() +
  labs(
    title    = "Standardized Mean Difference (Cohen's d)",
    subtitle = "Study 1 females (N=3,033) vs Study 2 females (N=50)\nDashed lines: |0.2| small, |0.5| medium, |0.8| large",
    x        = NULL,
    y        = "SMD (Study 1 − Study 2)",
    color    = NULL
  ) +
  theme_minimal() +
  theme(legend.position = "bottom")

ggsave("smd_plot.png", width = 8, height = 6, dpi = 300)
```

## Workshop participants

```{r workshop, echo=FALSE}
workshop$email <- tolower(str_trim(workshop$email))

# Merge data
workshop_demo <- workshop %>% left_join(analysis, by = "email")

# Recode
workshop_demo$Education <- as.character(workshop_demo$Education)
workshop_demo$Education[is.na(workshop_demo$Education)] <- "Prefer not to answer"
workshop_demo$Country[workshop_demo$Country == "United Kingdom of Great Britain and Northern Ireland"] <- "UK"
workshop_demo$Country[workshop_demo$Country == "United States of America"] <- "US"
workshop_demo <- workshop_demo %>% rename(Ethnicity = single_eth)

# Summary table 
# wd_table <- workshop_demo %>% select(Age,Country,single_eth, Education, Experience, Frequency) %>% arrange(Age)
# datatable(wd_table)
# wd_table %>% gt() %>% gtsave("workshop_demo.png")

wd_table <- workshop_demo %>%
  select(Age, Country, Ethnicity, Education, Experience, Frequency) %>%
  arrange(Age) %>%
  mutate(No = row_number()) %>%   # add numbering
  relocate(No)                    # move it to the first column

datatable(wd_table)

wd_table %>%
  gt() %>%
  gtsave("workshop_demo.png")
```

## Value Conflict: Frequency Tables shows that some value conflicts mirror Schwartz's value structure, while others show adjacent values can be in conflict -> values with psychological conflicts (motivational differences are positioned on opposite sides.
### Self-direction: Achievement/Power/Tradition
### Power: Conformity/Tradition/Stimulation 

```{r conflict_freq, echo=FALSE}
# self_conflict frequency table (Q23, both values combined)
self_freq <- bind_rows(
  analysis %>% select(Value = self_conflict_1),
  analysis %>% select(Value = self_conflict_2)
) %>%
  filter(!is.na(Value) & Value != "") %>%
  group_by(Value) %>%
  summarize(Frequency = n()) %>%
  arrange(desc(Frequency)) %>%
  mutate(
    Pct_of_mentions    = round(Frequency / sum(Frequency) * 100, 1),
    Pct_of_respondents = round(Frequency / nrow(analysis) * 100, 1)
  )

datatable(self_freq, caption = "Frequency Table: self_conflict (Q23)")
self_freq %>% gt() %>% gtsave("self_conflict_freq.png")

# power_conflict frequency table (Q79, both values combined)
power_freq <- bind_rows(
  analysis %>% select(Value = power_conflict_1),
  analysis %>% select(Value = power_conflict_2)
) %>%
  filter(!is.na(Value) & Value != "") %>%
  group_by(Value) %>%
  summarize(Frequency = n()) %>%
  arrange(desc(Frequency)) %>%
  mutate(
    Pct_of_mentions    = round(Frequency / sum(Frequency) * 100, 1),
    Pct_of_respondents = round(Frequency / nrow(analysis) * 100, 1)
  )

datatable(power_freq, caption = "Frequency Table: power_conflict (Q79)")
power_freq %>% gt() %>% gtsave("power_conflict_freq.png")
```

## Value Tension Network

```{r tension_network, echo=FALSE}
library(igraph)
library(ggraph)
library(patchwork)

# Color scheme
col_self       <- "#D55E00"  # Self-direction focal node: vermillion
col_power      <- "#0072B2"  # Power focal node: blue
col_other      <- "#BBBBBB"  # Other nodes: light gray
col_edge_self  <- "#E8935A"  # Self-direction edges: warm orange
col_edge_power <- "#6AAED6"  # Power edges: sky blue
col_edge_both  <- "#999999"  # Combined network edges (if shared)

# Helper: build edge list
build_edges <- function(col1, col2, focal_label) {
  bind_rows(
    analysis %>% select(target = .data[[col1]]),
    analysis %>% select(target = .data[[col2]])
  ) %>%
    filter(!is.na(target), target != "") %>%
    mutate(focal = focal_label) %>%
    filter(focal != target) %>%
    count(focal, target, name = "weight")
}

# Helper: single-focal network plot (star layout)
make_network_plot <- function(edges, focal_label, focal_color, edge_color, title) {
  g <- graph_from_data_frame(
    edges %>% rename(from = focal, to = target),
    directed = FALSE
  )
  V(g)$type <- ifelse(V(g)$name == focal_label, "Focal", "Other")
  center_idx <- which(V(g)$name == focal_label)

  set.seed(42)
  ggraph(g, layout = "star", center = center_idx) +
    geom_edge_link(aes(width = weight, alpha = weight), color = edge_color) +
    geom_node_point(aes(color = type, size = type)) +
    geom_node_text(aes(label = name), repel = TRUE,
                   size = 3.5, fontface = "bold", color = "#222222") +
    scale_edge_width(range = c(0.5, 5), name = "Frequency") +
    scale_edge_alpha(range = c(0.3, 1), guide = "none") +
    scale_color_manual(values = c("Focal" = focal_color, "Other" = col_other),
                       guide = "none") +
    scale_size_manual(values  = c("Focal" = 10, "Other" = 5),
                      guide = "none") +
    labs(title = title, subtitle = "Edge width = conflict frequency") +
    theme_graph(base_family = "sans")
}

# Build edge lists
self_edges  <- build_edges("self_conflict_1",  "self_conflict_2",  "Self-direction")
power_edges <- build_edges("power_conflict_1", "power_conflict_2", "Power")

# Individual networks
p_self  <- make_network_plot(self_edges,  "Self-direction", col_self,  col_edge_self,  "Self-direction Tensions")
p_power <- make_network_plot(power_edges, "Power",          col_power, col_edge_power, "Power Tensions")

# Combined network (FR layout, edges colored by focal value)
combined_edges <- bind_rows(self_edges, power_edges)
g_combined <- graph_from_data_frame(
  combined_edges %>% mutate(from = focal, to = target) %>%
    select(from, to, weight, focal),
  directed = FALSE
)
V(g_combined)$type <- case_when(
  V(g_combined)$name == "Self-direction" ~ "Self-direction",
  V(g_combined)$name == "Power"          ~ "Power",
  TRUE                                   ~ "Other"
)

# Custom layout: Self-direction left, Power right, others on a circle around them
all_nodes   <- V(g_combined)$name
other_nodes <- all_nodes[!all_nodes %in% c("Self-direction", "Power")]
n_other     <- length(other_nodes)
angles      <- seq(0, 2 * pi, length.out = n_other + 1)[-(n_other + 1)]
custom_layout <- data.frame(
  name = c("Self-direction", "Power", other_nodes),
  x    = c(-0.6, 0.6, 1.1 * cos(angles)),
  y    = c(0,    0,   1.1 * sin(angles))
) %>%
  mutate(
    x = case_when(
      name == "Security"     ~ x + 0.5,
      name == "Achievement"  ~ x - 0.4,
      name == "Universalism" ~ x - 0.4,
      name == "Benevolence" ~ x - 0.2,
      TRUE                   ~ x
    ),
    y = case_when(
      name == "Security"    ~ y - 0.5,
      name == "Achievement" ~ y - 0.5,
      name == "Power"       ~ y + 0.5,
      name == "Benevolence" ~ x + 0.5,
      TRUE                  ~ y
    )
  )
layout_mat <- as.matrix(custom_layout[match(all_nodes, custom_layout$name), c("x", "y")])

p_combined <- ggraph(g_combined, layout = layout_mat) +
  geom_edge_link(aes(width = weight, alpha = weight, color = focal)) +
  geom_node_point(aes(color = type, size = type)) +
  geom_node_label(aes(label = name),
                  color        = ifelse(V(g_combined)$type == "Self-direction", col_self,
                                 ifelse(V(g_combined)$type == "Power", col_power, "#333333")),
                  repel        = TRUE,
                  size         = 3.5,
                  fontface     = "bold",
                  fill         = "white",
                  label.size   = 0.2,
                  max.overlaps = Inf,
                  show.legend  = FALSE) +
  scale_edge_width(range = c(0.5, 5), name = "Frequency") +
  scale_edge_alpha(range = c(0.3, 1), guide = "none") +
  scale_edge_color_manual(
    values = c("Self-direction" = col_edge_self, "Power" = col_edge_power),
    guide  = "none"
  ) +
  scale_color_manual(
    values = c("Self-direction" = col_self, "Power" = col_power, "Other" = col_other),
    breaks = c("Self-direction", "Power", "Other"),
    name   = "Node"
  ) +
  scale_size_manual(values = c("Self-direction" = 10, "Power" = 10, "Other" = 5),
                    guide  = "none") +
  guides(
    edge_width = guide_legend(
      override.aes = list(edge_colour = "gray50", edge_alpha = 1)
    ),
    colour = guide_legend(
      override.aes = list(shape = 16, size = 5)
    )
  ) +
  labs(title    = "Combined Value Tension Network",
       subtitle = "Edge color = focal value; edge width = conflict frequency") +
  theme_graph(base_family = "sans") +
  theme(legend.position = "right")

# Preview before saving
p_self + p_power +
  plot_annotation(title   = "Value Tension Networks — Separate",
                  caption = "Node size: focal (large) vs other (small); edge width = conflict frequency")

p_combined

# Save separate networks image
ggsave("tension_network_separate.png",
       plot = p_self + p_power +
         plot_annotation(title   = "Value Tension Networks",
                         caption = "Node size: focal (large) vs other (small); edge width = conflict frequency"),
       width = 14, height = 7, dpi = 300)

# Save combined network image
ggsave("tension_network_combined.png",
       plot = p_combined,
       width = 10, height = 8, dpi = 300)

# Conflict frequency tables split by focal value
self_freq_net <- analysis %>%
  select(target = self_conflict_1, target2 = self_conflict_2) %>%
  pivot_longer(everything(), values_to = "Conflicting Value") %>%
  filter(!is.na(`Conflicting Value`), `Conflicting Value` != "") %>%
  count(`Conflicting Value`, name = "Frequency") %>%
  arrange(desc(Frequency))

power_freq_net <- analysis %>%
  select(target = power_conflict_1, target2 = power_conflict_2) %>%
  pivot_longer(everything(), values_to = "Conflicting Value") %>%
  filter(!is.na(`Conflicting Value`), `Conflicting Value` != "") %>%
  count(`Conflicting Value`, name = "Frequency") %>%
  arrange(desc(Frequency))

datatable(self_freq_net,  caption = "Conflict frequency: Self-direction")
datatable(power_freq_net, caption = "Conflict frequency: Power")

self_freq_net  %>% gt() %>% gtsave("conflict_freq_self.png")
power_freq_net %>% gt() %>% gtsave("conflict_freq_power.png")
```
