---
title: "GenAI"
author: "Ellie Jeong"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA,  warning = FALSE, message = FALSE)
knitr::opts_knit$set(root.dir = "Z:/usersurvey/_CSCW24")

library(readr)
library(dplyr)
library(tidyr)
library(reshape2)
library(ltm)
library(psych)
library(ggplot2)
library(ggsci)
library(data.table)
library(DT)
library(corrplot)
library(stringr)
library(mirt)

# get_os <- function(){
#   sysinf <- Sys.info()
#   if (!is.null(sysinf)){
#     os <- sysinf['sysname']
#     if (os == 'Darwin')
#       os <- "osx"
#   } else { ## mystery machine
#     os <- .Platform$OS.type
#     if (grepl("^darwin", R.version$os))
#       os <- "osx"
#     if (grepl("linux-gnu", R.version$os))
#       os <- "linux"
#   }
#   tolower(os)
# }
# 
# if(get_os() == "osx") {setwd("/Volumes/cbjackson2/usersurvey/_CSCW24/")} else
# {setwd("Z:/usersurvey/_CSCW24/")}
# survey <- read_csv("GenAI.csv",show_col_types = FALSE)

setwd("Z:/usersurvey/_CSCW24")
survey <- read_csv("Z:/usersurvey/_CSCW24/GenAI.csv",show_col_types = FALSE)
```

## Data cleaning: 124 valid responses

```{r}
survey_c <- survey[-c(1:2),]
survey_c <- survey_c[,-c(10:13)] #remove recipient name, reference, email
survey_c <- survey_c[which(survey_c$Status != "Survey Preview"),] #remove survey preview and spam
survey_c <- survey_c[which(survey_c$Status != "Spam"),]

#Remove duplication
#1. duplicate responses to open-end questions
survey_c <- survey_c[!duplicated(survey_c[,c("Q34","Q40","Q27","Q28")]),]
#2. there are 2 duplicate email address (expect 2 duplicates,NA)
dup_email <- survey_c %>% filter(duplicated(Q51) | duplicated(Q51, fromLast = TRUE)) 
survey_c <- survey_c[!duplicated(survey_c$Q51) | is.na(survey_c$Q51), ]
#3. keep duplicated IP address -> overall, responses are not identical (email address, open-end responses)
dup_ip <- survey_c %>% filter(duplicated(IPAddress) | duplicated(IPAddress, fromLast = TRUE))

#Exclusion criteria: no responses to section3 (values) & section4 (design aspirations)
survey_c <-survey_c %>% filter(!is.na(Q33_1))
```

## Descriptive statistics: frequency tables, bar graphs: 
  *Q12- How long have you worked as a software engineer? (group)
  
```{r}
t_Q12 <- datatable(survey_c %>% 
                    group_by(Q12) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_Q12 
```
  *Q13 - Which of the following tasks best describes the activities that you do/did in your role as a software engineer?

```{r}
task <- survey_c %>%
  separate_rows(Q13, sep = ",")
t_Q13 <- datatable(task %>% 
                    group_by(Q13) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_Q13
```
 
  *Q16- Have you used GenAI?
 
```{r}
# Q16- have you used GenAI?
##frequency table
use_t <- table(survey_c$Q16)  
use_t <- sort(use_t, decreasing = FALSE)

##Datatable
t_Q16 <- datatable(survey_c %>% 
                    group_by(Q16) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_Q16

##ggplot (https://emflant.tistory.com/293)
Q16_bar <- ggplot(survey_c, aes(x=factor(Q16)))+
  geom_bar(width=0.5, fill="darkblue")+
  theme_minimal() + labs(title="Experience of using GenAI tools for software engineering", x="Experience of using GenAI", y="Count") +
  geom_text(stat="count", aes(label=..count..),color = "white", vjust=1, hjust=1)+
  coord_flip() + scale_fill_aaas()  + theme(legend.position="none")
Q16_bar

## barplot
barplot(use_t, 
        horiz = TRUE,  
        main = "Experience of using GenAI tools for software engineering",
        xlim = c(0,120),
        ylim = c(0,5),
        width = 1,
        col = "darkblue",  
        border = "black",  
        names.arg = names(use_t),  
        las = 1,
        cex.names = 0.45,
        cex.axis = 0.45,
        space = 0.7,
        axes = FALSE)
axis(side=1,cex.axis = 0.45, at=seq(0,120,by=10))
```        

 *Q17-What GenAI tools have you used for software engineering work? (check all that
apply)
 
```{r}
tool <- survey_c %>%
  separate_rows(Q17, sep = ",")  # Adjust the separator to match your data
tool_t <- table(tool$Q17) 
tool_t <- sort(tool_t, decreasing = FALSE)


##Datatable
t_Q17 <- datatable(tool %>%  
                    group_by(Q17) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_Q17
```
  
  *Q19-What are/were your purposes for using GenAI tools in software engineering work? (check all that apply)
 
```{r} 
aim <- survey_c %>%
  separate_rows(Q19, sep = ",")  # Adjust the separator to match your data

##Datatable
t_Q19 <- datatable(aim %>%  
                    group_by(Q19) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_Q19

# #Split responses - does not work
# conditions <- survey_c$Q19 %in% "Self-evaluating performances based on the feedback/suggestions provided by GenAI tools (e.g., debugging)"
# survey_c$Q19[conditions] <- "Self-evaluating performances"
# survey_c$Q19 <- gsub("Self-evaluating performances based on the feedback/suggestions provided by GenAI tools (e.g., debugging)", "Self-evaluating performances", survey_c$Q19)
# library(stringr)
# survey_c$Q19 <- str_replace(survey_c$Q19, "Self-evaluating performances based on the feedback/suggestions provided by GenAI tools (e.g., debugging)", "Self-evaluating performances")
# recode values in r
# survey_c$Q19 <- dplyr::recode(survey_c$Q19, "Self-evaluating performances based on the feedback/suggestions provided by GenAI tools (e.g., debugging)" = "Self-evaluating performances")

```

  *Q20- How do you think the GenAI tools help you with software engineering work? (check all that apply

```{r}
benefit <- survey_c %>%
  separate_rows(Q20, sep = ",")  # Adjust the separator to match your data

##Datatable
t_Q20 <- datatable(benefit %>%  
                    group_by(Q20) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_Q20
```

  *Q21 - In the previous question you indicated that "I can attain knowledge and skills" when using GenAI tools. In what practices do you want to use GenAI tools for the purpose of attaining knowledge and skills for software engineering? (check all that apply)
```{r}
practice <- survey_c %>%
  separate_rows(Q21, sep = ",")  # Adjust the separator to match your data

##Datatable
t_Q21 <- datatable(practice %>%  
                    group_by(Q21) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_Q21
```  
  
  *Q23 - In the previous question you indicated that "I can attain knowledge and skills" when using GenAI tools. What kind of knowledge and skills for software engineering work do you want to learn through the GenAI tools? (check all that apply)

```{r}
skill <- survey_c %>%
  separate_rows(Q23, sep = ",")  # Adjust the separator to match your data

##Datatable
t_Q23 <- datatable(skill %>%  
                    group_by(Q23) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_Q23
```

  *Q24 - In the previous question you did not indicate "I can attain knowledge and skills"when using GenAI tools. Have you ever felt the need to attain knowledge and skills for software engineering work?

```{r}
t_Q24 <- datatable(survey_c %>%  
                    group_by(Q24) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_Q24
```

  *Q25 - For what practices do you feel the need to attain knowledge and skills for software engineering work? (check all that apply)
```{r}  
practice_2 <- survey_c %>%
  separate_rows(Q25, sep = ",")  # Adjust the separator to match your data

##Datatable
t_Q25 <- datatable(practice_2 %>%  
                    group_by(Q25) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_Q25  
```


  *Q26 - What kind of knowledge and skills do you feel the need to learn for software
engineering work? (check all that apply)

```{r}
skill_2 <- survey_c %>%
  separate_rows(Q26, sep = ",")  # Adjust the separator to match your data

##Datatable
t_Q26 <- datatable(skill_2 %>%  
                    group_by(Q26) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_Q26 
```

 * Q33 - Rate the level of importance of each of following items when considering the use of GenAI tools in learning (e.g., attaining knowledge and skills) during software engineering work (1: not important at all, 5: very important).
```{r}
# List of column names you want to convert to numeric
columns_to_convert <- c("Q33_1", "Q33_2", "Q33_3", "Q33_4", "Q33_5", "Q33_6", "Q33_7", "Q33_8", "Q33_9", "Q33_10", "Q33_11")

# Convert the specified columns to numeric
survey_c <- survey_c %>%
  mutate_at(vars(all_of(columns_to_convert)), as.numeric)

accountability <- survey_c %>%
  filter(!is.na(Q33_1)) %>% 
  summarize(
    Min = min(`Q33_1`, na.rm = TRUE),   
    Max = max(`Q33_1`, na.rm = TRUE),   
    Mean = mean(`Q33_1`, na.rm = TRUE), 
    SD = sd(`Q33_1`, na.rm = TRUE),    
    Variance = var(`Q33_1`, na.rm = TRUE), 
    Count = n()
  )
accountability
```

### Compare responses of different user groups: 

```{r pressure, echo=FALSE}

#mosaic plot
table <- table(survey_c$Q45, survey_c$Q36)
mosaicplot(table,
  main = "Mosaic plot",
  color = TRUE
)

```

## Chi-square test

```{r}
#Chi-square test
eth_timing <- chisq.test(survey_c$Q45, survey_c$Q36, correct=FALSE)
# printing the p-value
eth_timing$p.value
# printing the mean
eth_timing$estimate

#Fisher's exact test (Fisher’s exact test is used when there is at least one cell in the contingency table of the expected frequencies below 5)
#https://statsandr.com/blog/fisher-s-exact-test-in-r-independence-test-for-a-small-sample/
test <- fisher.test(dataframe)
```
