---
title: "GenAI"
author: "Ellie Jeong"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA,  warning = FALSE, message = FALSE)
#knitr::opts_knit$set(root.dir = "Z:/usersurvey/_CSCW24")

library(readr)
library(dplyr)
library(tidyr)
library(reshape2)
library(ltm)
library(psych)
library(ggplot2)
library(ggsci)
library(data.table)
library(DT)
library(corrplot)
library(stringr)
library(mirt)
library(reshape2)
library(tidyverse)
library(wordcloud)
library(car)

get_os <- function(){
  sysinf <- Sys.info()
  if (!is.null(sysinf)){
    os <- sysinf['sysname']
    if (os == 'Darwin')
      os <- "osx"
  } else { ## mystery machine
    os <- .Platform$OS.type
    if (grepl("^darwin", R.version$os))
      os <- "osx"
    if (grepl("linux-gnu", R.version$os))
      os <- "linux"
  }
  tolower(os)
}

if(get_os() == "osx") {setwd("/Volumes/cbjackson2/usersurvey/_CSCW24/")} else
{setwd("Z:/usersurvey/_CSCW24/")}
survey <- read_csv("GenAI.csv",show_col_types = FALSE)

# setwd("Z:/usersurvey/_CSCW24")
# survey <- read_csv("Z:/usersurvey/_CSCW24/GenAI.csv",show_col_types = FALSE)
```

## Data cleaning: 123 valid responses

```{r}
survey_c <- survey[-c(1:2),]
survey_c <- survey_c[,-c(10:13)] #remove recipient name, reference, email
survey_c <- survey_c[which(survey_c$Status != "Survey Preview"),] #remove survey preview and spam
survey_c <- survey_c[which(survey_c$Status != "Spam"),]

#Remove duplication
#1. identical responses to open-end questions (153 obs)
col <- c("Q34", "Q40", "Q27", "Q28")
dup_q <- survey_c[duplicated(survey_c[col]) | duplicated(survey_c[col], fromLast = TRUE), ]
survey_c <- survey_c %>%
  filter(!duplicated(survey_c[col]) & !duplicated(survey_c[col], fromLast = TRUE))
#survey_c <- survey_c[!duplicated(survey_c[,c("Q34","Q40","Q27","Q28")]),]

#2. identical email address (4 obs except for NAs)
dup_email <- survey_c %>% filter(duplicated(Q51) | duplicated(Q51, fromLast = TRUE)) 
filtered_survey_c <- survey_c %>%
  filter(is.na(Q51)|!duplicated(Q51) | !duplicated(Q51, fromLast = TRUE))

#3. keep duplicated IP address -> overall, responses are not identical (email address, open-end responses)
dup_ip <- survey_c %>% filter(duplicated(IPAddress) | duplicated(IPAddress, fromLast = TRUE))

#Exclusion criteria: no responses to section3 (values) & section4 (design aspirations)
survey_c <-survey_c %>% filter(!is.na(Q33_1))
```

## Descriptive statistics: frequency table, bar graph, pie chart    
### Findings 
  * Experiences and needs for learning
    + Responses show that SE are helpful with learning as well as improving task performance. 
    + The majority of respondents found GenAI most helpful with learning (attaining knowledge and skills) at workplaces. 
    + Even people who have not thought about learning felt the need to attain knowledge and skills through GenAI.
  * Usage patterns
    + The majority of SEs have experience in using diverse GenAI tools for workplace learning. 
    + SEs often use various Gen AI tools when working.
  * Needs (goals, values, design aspirations) and challenges
    + Responses show more diverse needs for GenAI that can be adopted in various phases of SE. 
    + More user-centered needs and usage patterns (e.g., attain knowledge and skills, self-evaluating performances, decision-making) compared to task-centered needs that previous findings show (e.g., quickly executable assistance - solving problems, needs for documents and templates, finding information). 
    + As GenAI is applied to diverse tasks and contexts, new types of needs (e.g., privacy, flexibility) emerge besides those related to performances (accuracy, reliability)   

### Demographics
    * Q42 - What is your age?
  
```{r, echo=FALSE}
t_q42 <- datatable(survey_c %>% 
                    group_by(Q42) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_q42 

# Create a data frame for charts
df_q42 <- survey_c %>%
  group_by(Q42) %>%
  summarise(freq = n()) %>%
  arrange(desc(freq)) %>%
  mutate(percent = round(freq / sum(freq),digits = 2))

#bar graph
b_q42 <- ggplot(data = df_q42, aes(x = reorder(Q42, freq), y = freq)) +
  geom_bar(stat = "identity", width = 0.5, fill = "darkblue") +
  theme_minimal() +
  labs(title = "Distribution of age", x = "age", y = "Count") +
  geom_text(aes(label = freq), color = "white", vjust = 1, hjust = 1.7, size = 3.5) +
  scale_fill_manual(values = "darkblue") +
  theme(legend.position = "none") +
  coord_flip() + scale_fill_aaas()  + theme(legend.position="none")
b_q42

# Create the pie chart
p_q42 <- ggplot(data = df_q42, aes(x = "", y = percent, fill = Q42)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y") +
  labs(title = "Distribution of age") +
  theme_void() +
  geom_text(aes(label = paste0(round(percent*100), '%')),
            position = position_stack(vjust = 0.5), size = 3) 
#+ scale_fill_brewer(palette = "Blues")

p_q42
```
 
    * Q43 - How do you identify your gender?
  
```{r, echo=FALSE}
t_q43 <- datatable(survey_c %>% 
                    group_by(Q43) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_q43 

# Create a data frame for charts
df_q43 <- survey_c %>%
  group_by(Q43) %>%
  summarise(freq = n()) %>%
  arrange(desc(freq)) %>%
  mutate(percent = round(freq / sum(freq),digits = 2))

#bar graph
b_q43 <- ggplot(data = df_q43, aes(x = reorder(Q43, freq), y = freq)) +
  geom_bar(stat = "identity", width = 0.5, fill = "darkblue") +
  theme_minimal() +
  labs(title = "Distribution of gender", x = "gender", y = "Count") +
  geom_text(aes(label = freq), color = "white", vjust = 1, hjust = 1.7, size = 3.5) +
  scale_fill_manual(values = "darkblue") +
  theme(legend.position = "none") +
  coord_flip() + scale_fill_aaas()  + theme(legend.position="none")
b_q43

# Create the pie chart
p_q43 <- ggplot(data = df_q43, aes(x = "", y = percent, fill = Q43)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y") +
  labs(title = "Distribution of gender") +
  theme_void() +
  geom_text(aes(label = paste0(round(percent*100), '%')),
            position = position_stack(vjust = 0.5), size = 3) 
#+ scale_fill_brewer(palette = "Blues")

p_q43
```  
    
    * Q45 - How would you best describe your race/ethnicity?
  
```{r, echo=FALSE}
eth <- survey_c %>%
  separate_rows(Q45, sep = ",") 
t_q45 <- datatable(eth %>% 
                    group_by(Q45) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_q45 

# Create a data frame for charts
df_q45 <- survey_c %>%
  group_by(Q45) %>%
  summarise(freq = n()) %>%
  arrange(desc(freq)) %>%
  mutate(percent = round(freq / sum(freq),digits = 2))

#bar graph
b_q45 <- ggplot(data = df_q45, aes(x = reorder(Q45, freq), y = freq)) +
  geom_bar(stat = "identity", width = 0.5, fill = "darkblue") +
  theme_minimal() +
  labs(title = "Distribution of ethnicity", x = "ethnicity", y = "Count") +
  geom_text(aes(label = freq), color = "white", vjust = 1, hjust = 1.7, size = 2.7) +
  scale_fill_manual(values = "darkblue") +
  theme(legend.position = "none") +
  coord_flip() + scale_fill_aaas()  + theme(legend.position="none")
b_q45

# Create the pie chart
p_q45 <- ggplot(data = df_q45, aes(x = "", y = percent, fill = Q45)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y") +
  labs(title = "Distribution of ethnicity") +
  theme_void() +
  geom_text(aes(label = paste0(round(percent*100), '%')),
            position = position_stack(vjust = 0.5), size = 2) 
#+ scale_fill_brewer(palette = "Blues")
p_q45
```  
    
    * Q46 - What is your highest level of education?
  
```{r, echo=FALSE}
t_q46 <- datatable(survey_c %>% 
                    group_by(Q46) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_q46 

# Create a data frame for charts
df_q46 <- survey_c %>%
  group_by(Q46) %>%
  summarise(freq = n()) %>%
  arrange(desc(freq)) %>%
  mutate(percent = round(freq / sum(freq),digits = 2))

#bar graph
b_q46 <- ggplot(data = df_q46, aes(x = reorder(Q46, freq), y = freq)) +
  geom_bar(stat = "identity", width = 0.5, fill = "darkblue") +
  theme_minimal() +
  labs(title = "Distribution of education level", x = "education level", y = "Count") +
  geom_text(aes(label = freq), color = "white", vjust = 1, hjust = 1.7, size = 2.7) +
  scale_fill_manual(values = "darkblue") +
  theme(legend.position = "none") +
  coord_flip() + scale_fill_aaas()  + theme(legend.position="none")
b_q46

# Create the pie chart
p_q46 <- ggplot(data = df_q46, aes(x = "", y = percent, fill = Q46)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y") +
  labs(title = "Distribution of education level") +
  theme_void() +
  geom_text(aes(label = paste0(round(percent*100), '%')),
            position = position_stack(vjust = 0.5), size = 3) 
#+ scale_fill_brewer(palette = "Blues")
p_q46
```    
    
    *    Q4 - Are you currently located in the United States?
  
```{r, echo=FALSE}
t_q4 <- datatable(survey_c %>% 
                    group_by(Q4) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_q4
```
    
    * Q5 - Which of the following categories best describes your current employment status?
  
```{r, echo=FALSE}
t_q5 <- datatable(survey_c %>% 
                    group_by(Q5) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_q5
```  
    
    * Q6 - How would you classify your most recent Computer and Information Technology
job? (check all that apply)
  
```{r, echo=FALSE}
job <- survey_c %>%
  separate_rows(Q6, sep = ",") 
t_q6 <- datatable(job %>% 
                    group_by(Q6) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_q6
```
    
    * Q11 - How would you classify the industry where you worked most recently as a software
engineer? (check all that apply)
  
```{r, echo=FALSE}
industry <- survey_c %>%
  separate_rows(Q11, sep = ",")
t_q11 <- datatable(industry %>% 
                    group_by(Q11) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_q11
```  

  
    * Q12- How long have you worked as a software engineer?
  
```{r, echo=FALSE}
t_q12 <- datatable(survey_c %>% 
                    group_by(Q12) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_q12 

# Create a data frame for charts
df_q12 <- survey_c %>%
  group_by(Q12) %>%
  summarise(freq = n()) %>%
  arrange(desc(freq)) %>%
  mutate(percent = round(freq / sum(freq),digits = 2))

#bar graph
b_q12 <- ggplot(data = df_q12, aes(x = reorder(Q12, freq), y = freq)) +
  geom_bar(stat = "identity", width = 0.5, fill = "darkblue") +
  theme_minimal() +
  labs(title = "Distribution of work years", x = "work years", y = "Count") +
  geom_text(aes(label = freq), color = "white", vjust = 1, hjust = 1.5, size = 3) +
  scale_fill_manual(values = "darkblue") +
  theme(legend.position = "none") +
  coord_flip() + scale_fill_aaas()  + theme(legend.position="none")
b_q12

# Create the pie chart
p_q12 <- ggplot(data = df_q12, aes(x = "", y = percent, fill = Q12)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar(theta = "y") +
  labs(title = "Distribution of work years") +
  theme_void() +
  geom_text(aes(label = paste0(round(percent*100), '%')),
            position = position_stack(vjust = 0.5), size = 2)
#+ scale_fill_brewer(palette = "Spectral")

p_q12
```

    * Q13 - Which of the following tasks best describes the activities that you do/did in your role as a software engineer?

```{r, echo=FALSE}
task <- survey_c %>%
  separate_rows(Q13, sep = ",")
t_Q13 <- datatable(task %>% 
                    group_by(Q13) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_Q13
```

### Usage patterns  

    * Q16- Have you used GenAI?
 
```{r, echo=FALSE}
# Q16- have you used GenAI?
##frequency table
use_t <- table(survey_c$Q16)  
use_t <- sort(use_t, decreasing = FALSE)

##Data table
t_Q16 <- datatable(survey_c %>% 
                    group_by(Q16) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_Q16
```        

    * Q17-What GenAI tools have you used for software engineering work? (check all that
apply)
 
```{r, echo=FALSE}
tool <- survey_c %>%
  separate_rows(Q17, sep = ",")  # Adjust the separator to match your data
tool_t <- table(tool$Q17) 
tool_t <- sort(tool_t, decreasing = FALSE)


##Data table
t_Q17 <- datatable(tool %>%  
                    group_by(Q17) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_Q17
```
    
    * Q22 - What GenAI tools have you used to attain knowledge and skills for software
engineering work? (check all that apply)
  
```{r, echo=FALSE}
tool <- survey_c %>%
  separate_rows(Q22, sep = ",") 
t_q22 <- datatable(tool %>% 
                    filter(!is.na(Q22)) %>%
                    group_by(Q22) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_q22
```  

    * Q18 - How often do/did you use GenAI tools for software engineering work? (na=have not used GenAI)
  
```{r, echo=FALSE}
#remove na (1)
t_q18 <- datatable(survey_c %>% 
                    filter(!is.na(Q18)) %>% 
                    group_by(Q18) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_q18
```    

### Needs - Goals  

    * Q19-What are/were your purposes for using GenAI tools in software engineering work? (check all that apply)
 
```{r, echo=FALSE} 
aim <- survey_c %>%
  separate_rows(Q19, sep = ",")  # Adjust the separator to match your data

##Datatable
t_Q19 <- datatable(aim %>%  
                    filter(!is.na(Q19)) %>%
                    group_by(Q19) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_Q19
```

    * Q20- How do you think the GenAI tools help you with software engineering work? (check all that apply

```{r, echo=FALSE}
benefit <- survey_c %>%
  separate_rows(Q20, sep = ",")  # Adjust the separator to match your data

##Data table
t_Q20 <- datatable(benefit %>%  
                     filter(!is.na(Q20)) %>%
                    group_by(Q20) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_Q20
```


    * Q21 - In the previous question you indicated that "I can attain knowledge and skills" when using GenAI tools. In what practices do you want to use GenAI tools for the purpose of attaining knowledge and skills for software engineering? (check all that apply)
  
```{r, echo=FALSE}
practice <- survey_c %>%
  separate_rows(Q21, sep = ",")  # Adjust the separator to match your data

##Data table
t_Q21 <- datatable(practice %>%  
                    filter(!is.na(Q21)) %>%
                    group_by(Q21) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_Q21
```  
  
    * Q23 - In the previous question you indicated that "I can attain knowledge and skills" when using GenAI tools. What kind of knowledge and skills for software engineering work do you want to learn through the GenAI tools? (check all that apply)

```{r, echo=FALSE}
skill <- survey_c %>%
  separate_rows(Q23, sep = ",")  # Adjust the separator to match your data

##Data table
t_Q23 <- datatable(skill %>%  
                    filter(!is.na(Q23)) %>%
                    group_by(Q23) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_Q23
```


    * Q24 - In the previous question you did not indicate "I can attain knowledge and skills"when using GenAI tools. Have you ever felt the need to attain knowledge and skills for software engineering work?

```{r, echo=FALSE}
t_Q24 <- datatable(survey_c %>% 
                    filter(!is.na(Q24)) %>%
                    group_by(Q24) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_Q24
```

    * Q25 - For what practices do you feel the need to attain knowledge and skills for software engineering work? (check all that apply)
  
```{r, echo=FALSE}  
practice_2 <- survey_c %>%
  separate_rows(Q25, sep = ",")  # Adjust the separator to match your data

##Data table
t_Q25 <- datatable(practice_2 %>%  
                    filter(!is.na(Q25)) %>%
                    group_by(Q25) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_Q25  
```


    * Q26 - What kind of knowledge and skills do you feel the need to learn for software
engineering work? (check all that apply)

```{r, echo=FALSE}
skill_2 <- survey_c %>%
  separate_rows(Q26, sep = ",")  # Adjust the separator to match your data

##Data table
t_Q26 <- datatable(skill_2 %>% 
                    filter(!is.na(Q26)) %>%
                    group_by(Q26) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_Q26 
```


### Needs - values  

    * Q33 - Rate the level of importance of each of following items when considering the use of GenAI tools in learning (e.g., attaining knowledge and skills) during software engineering work (1: not important at all, 5: very important).
 
```{r, echo=FALSE}
# List of column names you want to convert to numeric
columns_to_convert <- c("Q33_1", "Q33_2", "Q33_3", "Q33_4", "Q33_5", "Q33_6", "Q33_7", "Q33_8", "Q33_9", "Q33_10", "Q33_11")
survey_c <- survey_c %>%
  mutate_at(vars(all_of(columns_to_convert)), as.numeric)

summary_stats <- sapply(survey_c[, columns_to_convert], function(x) c(
  round(min(x), digits = 2),
  round(max(x), digits = 2),
  round(mean(x), digits = 2),
  round(sd(x), digits = 2),
  round(var(x), digits = 2)
))
summary_stats <- as.data.frame(summary_stats)
col_stat <- c("Accountability","Reliability","Transparency","Fairness", "Privacy","Security","Safety","Autonomy","Flexibility","Accessibility","Customization")
colnames(summary_stats) <- col_stat
row_stat <- c("Min","Max","Mean","StandardDeviation","Variance")
rownames(summary_stats) <- row_stat
datatable(summary_stats)

# Reshape the data into a long format
summary_stats_long <- summary_stats %>%
  rownames_to_column(var = "Statistic") %>%
  pivot_longer(cols = -Statistic, names_to = "Variable", values_to = "Value")

# Create a grouped bar graph
grouped_bar <- ggplot(summary_stats_long, aes(x = Variable, y = Value, fill = Statistic)) +
  geom_bar(stat = "identity", position = "dodge", width = 0.7) +
  labs(title = "Values Statistics",
       x = "value",
       y = "score") +
  theme_minimal()
grouped_bar
```

### Needs - Design aspirations

    * Q36 - When do you want the GenAI tools to assist you in learning knowledge and skills
for software engineering work? (check all that apply)

```{r, echo=FALSE}
q36 <- survey_c %>%
  separate_rows(Q36, sep = ",")  # Adjust the separator to match your data

##Data table
t_q36 <- datatable(q36 %>%  
                    group_by(Q36) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_q36 
```


    * Q37 - How do you want the GenAI tools to assist you in learning knowledge and skills for software engineering work? (check all that apply)

```{r, echo=FALSE}
q37 <- survey_c %>%
  separate_rows(Q37, sep = ",")  # Adjust the separator to match your data

##Data table
t_q37 <- datatable(q37 %>%  
                    group_by(Q37) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_q37 

```


    * Q38 -  Where do you want the GenAI tools to offer assistance for learning knowledge and skills for software engineering work? (e.g., information wrapped in tooltips)? (check all that apply)

```{r, echo=FALSE}
q38 <- survey_c %>%
  separate_rows(Q38, sep = ",")  # Adjust the separator to match your data

##Data table
t_q38 <- datatable(q38 %>%  
                    group_by(Q38) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_q38
```
 

    * Q39 -  Which aspects of learning for software engineering work can be improved more by the assistance of GenAI? (check all that apply)

```{r, echo=FALSE}
q39 <- survey_c %>%
  separate_rows(Q39, sep = ",")  # Adjust the separator to match your data

##Data table
t_q39 <- datatable(q39 %>%  
                    group_by(Q39) %>% 
                    tally() %>%
                    arrange(desc(n)) %>%
                    mutate(freq = round(n / sum(n),digits=2)))
t_q39
```

### Wordcloud - open-end questions
 
    * Q27 - What specific reasons do you have for not using GenAI technologies to learn new skills and information for software engineering work?

```{r}
q27 <- survey_c[,c("Q27")] 
wc_q27 <-table(q27) 
temp27<- sort(wc_q27, decreasing=T)
pal <- brewer.pal(8, "Dark2")
set.seed(405)
wordcloud(words = names(temp27), 
          freq = temp27, 
          min.freq = 1, 
          max.words = Inf, 
          random.order = FALSE, 
          random.color = TRUE, 
          rot.per = 0.1, 
          scale = c(8, 0.2), 
          colors = pal) 
```
 
    * Q28 - What other tools or methods do you use to attain knowledge and skills for software engineering work?

```{r}
q28 <- survey_c[,c("Q28")] 
wc_q28 <-table(q28)
temp28<- sort(wc_q28, decreasing=T)
pal <- brewer.pal(8, "Dark2")
set.seed(405)
wordcloud(words = names(temp28), 
          freq = temp28, 
          min.freq = 1, 
          max.words = Inf, 
          random.order = FALSE, 
          random.color = TRUE, 
          rot.per = 0.1, 
          scale = c(8, 0.2), 
          colors = pal) 
```
 
    * Q34 - What other aspects are important for the use of GenAI to attain knowledge and skills for software engineering work?

```{r}
q34 <- survey_c[,c("Q34")] 
wc_q34 <-table(q34)
temp34<- sort(wc_q34, decreasing=T)
pal <- brewer.pal(8, "Dark2")
set.seed(405)
wordcloud(words = names(temp34), 
          freq = temp34, 
          min.freq = 1, 
          max.words = Inf, 
          random.order = FALSE, 
          random.color = TRUE, 
          rot.per = 0.1, 
          scale = c(8, 0.2), 
          colors = pal) 
```

    * Q40 - What other challenges have you faced when using GenAI tools for learning at the
workplace as a software engineer?

```{r}
q40 <- survey_c[,c("Q40")] 
wc_q40 <-table(q40)
temp40<- sort(wc_q40, decreasing=T)
pal <- brewer.pal(8, "Dark2")
set.seed(405)
wordcloud(words = names(temp40), 
          freq = temp40, 
          min.freq = 1, 
          max.words = Inf, 
          random.order = FALSE, 
          random.color = TRUE, 
          rot.per = 0.1, 
          scale = c(8, 0.2), 
          colors = pal) 
```

## Compare GenAI experiences & needs between different user groups
### Findings
  * There is a significant relationship between work years and frequency of using GenAI.
  * No other statistical test shows the relationship between work years and user experiences and needs.
  * Q12. SE Work years - experience of using GenAI/frequency of using GenAI/purpose of using GenAI/GenAI tools they use/knowledge and skills they want to learn/values rating/design aspirations
   

```{r pressure}
##work years - experience of using GenAI
#Bar graph
#https://m.blog.naver.com/regenesis90/222203543999
q16 <- survey_c %>% filter(!is.na(Q16))
ggplot(q16,
       aes(x=Q12,
           fill=Q16))+
  geom_bar(position='fill')+
  coord_flip() +
  labs(x = "work years", y = "experience of using GenAI", fill = "experience of using GenAI")

#Chi-square test (test of independence: If your data fails the sample size assumption, try collapsing categories to increase the expected frequencies. If that is not possible, an alternative test is Fisher’s Exact test.)
t_q12q16 <- table(survey_c$Q12, survey_c$Q16)
chisq.test(t_q12q16)$expected
chisq.test(t_q12q16,correct=FALSE)

fisher.test(t_q12q16) #p-value = 1

##work years - frequency of using GenAI
#Bar graph
q18 <- survey_c %>% filter(!is.na(Q18))
ggplot(q18,
       aes(x=Q12,
           fill=Q18))+
  geom_bar(position='fill')+
  coord_flip() +
  labs(x = "work years", y = "frequency of using GenAI", fill = "frequency of using GenAI")

#Chi-square test
t_q12q18 <- table(survey_c$Q12, survey_c$Q18)
chisq.test(t_q12q18)$expected
chisq.test(t_q12q18,correct=FALSE)

fisher.test(t_q12q18) #p-value = 0.01012

##work years - purpose of using GenAI
practice3 <- practice %>% filter(!is.na(Q21)) 
t_q12q21 <- table(practice3$Q12, practice3$Q21)
chisq.test(t_q12q21)$expected
chisq.test(t_q12q21,correct=FALSE)

fisher.test(t_q12q21, simulate.p.value = TRUE) #p-value = 1

##work years - GenAI tools
tool3 <- tool %>% filter(!is.na(Q22)) 
t_q12q22 <- table(tool3$Q12, tool3$Q22)
chisq.test(t_q12q22)$expected
chisq.test(t_q12q22,correct=FALSE)

fisher.test(t_q12q22, simulate.p.value = TRUE) #p-value = 0.9995

##work years - knowledge and skills
skill3 <- skill %>% filter(!is.na(Q23)) 
t_q12q23 <- table(skill3$Q12, skill3$Q23)
chisq.test(t_q12q23)$expected
chisq.test(t_q12q23,correct=FALSE)

fisher.test(t_q12q23, simulate.p.value = TRUE) #p-value = 0.9945

##work years - accountability rating
#mean value
survey_c %>%
  group_by(Q12) %>%
  summarise(Mean_Q33_1 = mean(Q33_1, na.rm = TRUE),
            Mean_Q33_2 = mean(Q33_2, na.rm = TRUE),
            Mean_Q33_3 = mean(Q33_3, na.rm = TRUE),
            Mean_Q33_4 = mean(Q33_4, na.rm = TRUE),
            Mean_Q33_5 = mean(Q33_5, na.rm = TRUE),
            Mean_Q33_6 = mean(Q33_6, na.rm = TRUE),
            Mean_Q33_7 = mean(Q33_7, na.rm = TRUE),
            Mean_Q33_8 = mean(Q33_8, na.rm = TRUE),
            Mean_Q33_9 = mean(Q33_9, na.rm = TRUE),
            Mean_Q33_10 = mean(Q33_10, na.rm = TRUE),
            Mean_Q33_11 = mean(Q33_11, na.rm = TRUE)
            )

#ANOVA (does not satisfy assumptions)
boxplot(survey_c$Q33_1~survey_c$Q12)
leveneTest(survey_c$Q33_1~survey_c$Q12)
aov_q12_1 <- aov(survey_c$Q33_1~survey_c$Q12)
aov_q12_1
TukeyHSD(aov_q12_1)
#Kruskal-Wallis (KW) test: nonparametric test based on ranks
kruskal.test(survey_c$Q33_1~survey_c$Q12)
```

    * Q11. Industry where SE works - experience of using GenAI/frequency of using GenAI/purpose of using GenAI/GenAI tools they use/knowledge and skills they want to learn/values rating/design aspirations
  
    * Q13. Task SE conducts - experience of using GenAI/frequency of using GenAI/purpose of using GenAI/GenAI tools they use/knowledge and skills they want to learn/values rating/design aspirations
  
    * Demograhpic feature (age, gender, ethnicity, education level) - experience of using GenAI/frequency of using GenAI/purpose of using GenAI/GenAI tools they use/knowledge and skills they want to learn/values rating/design aspirations
